---
title: "Thesis ADAM Analysis 1"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

# Compiling data, restructuring, and plotting asynchronies

ADAM model parameter estimates were computed in Matlab script:

ThesisADAM_boundedresults.m Output is one file which includes participant and condition identifiers, a
range of performance measures, and parameter estimates for the
'Adaptation-only' and 'Full' versions of ADAM. Log-likelihood estimates
are also included for each model version, indicating quality of model
fit to data (higher values [less -vs/more +ve] mean better fit)

Adaptation-only version includes estimates of: 
- Phase Correction ('Adapt_Alpha') 
- Period Correction ('Adapt_Beta') 
- Timekeeper Noise ('Adapt_Tn') 
- Motor Noise ('Adapt_Mn')

Joint version of ADAM includes estimates of: 
- Period correction ('Joint_Beta') 
- Temporal Prediction ('Joint_Delta') 
- Anticipatory Error Correction ('Joint_Gamma') 
- Timekeeper Noise ('Joint_Tn')

Note that the ADAM parameter estimation procedure is run twice per data
set with TARGET musician (the one for which parameters are being
estimated) and REFERENCE musician (the one for which parameters are NOT
being estimated) swapped so estimates are given for each musician.

### Set directory where to read and write files

```{r}
setwd("C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis") # NEED TO SET TO CURRENT PATH
```

### Load libraries

```{r}
library(bestNormalize)
library(caret)
library(dplyr)
library(emmeans)
library(flextable)
library(ggeffects)
library(ggplot2)
library(ggpp) # for jitternudge [not currently used]
library(ggpubr)
library(ggsci) # For Raincloud plots
library(grid)
library(gridExtra)
library(gtools)
library(huxtable)
library(broom.mixed)
library(lme4) # For lmer
library(lmerTest) # Alternative for lmer that gives p-values/asterisks. Automatically updates output of lmer (just load here, no need to call below) 
library(reshape2)
library(rstatix)
library(stats) # For confint
library(tidyr)
library(tidyverse)
library(readxl)
library(CRSSIO) # This has additional custom editing features for boxplot
```

### SD of signed asynchronies

```{r}
DV_Async <- as.symbol('SD_Signed_Async')
```

### Extract ID, Song, Artist, N_Events, Mean ITI, & CV ITI info for each sequence (for reporting in table) for both conditions

```{r}
all_data <- read_excel("C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/ThesisADAM_boundedresults.xlsx")
all_data <- all_data %>% mutate_all(~ifelse(is.nan(.), NA, .)) # Convert NaNs to NA
all_data$DV_Async <- all_data[[DV_Async]]

# Extract Pair, Code, `Lead/Phrase, N_Events, Mean ITI, & CV ITI info for each sequence (for reporting in table)
all_info <- all_data[1:(nrow(all_data)), c('ID', 'Song', 'Artist', 'Tempo', 'IOI Entropy', 'N_Events', 'Mn_ITI', 'CV_ITI')]
colnames(all_info) <- c('ID', 'Song', 'Artist', 'Tempo', 'IOI Entropy', 'N events', 'Mean Interval (s)', 'CV Interval (prop.)')
```

### Make table

```{r}
# Order the table
all_info_order <- all_info[order(all_info$ID, all_info$Song, all_info$Artist), ]

# Format as a flextable
all_info.ft <- flextable(all_info_order)
all_info.ft <- colformat_double(all_info.ft, digits = 2)

# Export to Word document
save_as_docx(all_info.ft, path = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 1/Results/Sequence_Info_Unfiltered.docx")
```

### Filter information table for each section for outliers

```{r}
# FILTER REAL CONDITION
# Add column to indicate outliers based on asynchronies
all_data$Outlier_Async <- 0
outCrit <- 3 # Set outlier criterion: How many times IQR

all_data$DV_Async <- as.numeric(as.character(all_data$DV_Async))
qnt <- quantile(all_data$DV_Async, probs=c(.25, .75), na.rm = TRUE)
H <- outCrit * IQR(all_data$DV_Async, na.rm = TRUE)
y <- all_data$Outlier_Async
y[all_data$DV_Async < (qnt[1] - H)] <- 1
y[all_data$DV_Async > (qnt[2] + H)] <- 1
y
all_data$Outlier_Async <- y

# Add column to indicate outliers based on temporal prediction (delta)
all_data$Outlier_Alpha <- 0

all_data$Adapt_Alpha <- as.numeric(as.character(all_data$Adapt_Alpha))
qntA <- quantile(all_data$Adapt_Alpha, probs=c(.25, .75), na.rm = TRUE)
HA <- outCrit * IQR(all_data$Adapt_Alpha, na.rm = TRUE)
yA <- all_data$Outlier_Alpha
yA[all_data$Adapt_Alpha < (qntA[1] - HA)] <- 1
yA[all_data$Adapt_Alpha > (qntA[2] + HA)] <- 1
yA
all_data$Outlier_Alpha <- yA

# Add column to indicate outliers based on temporal prediction (delta)
all_data$Outlier_Delta <- 0

all_data$Joint_Delta <- as.numeric(as.character(all_data$Joint_Delta))
qntD <- quantile(all_data$Joint_Delta, probs=c(.25, .75), na.rm = TRUE)
HD <- outCrit * IQR(all_data$Joint_Delta, na.rm = TRUE)
yD <- all_data$Outlier_Delta
yD[all_data$Joint_Delta < (qntD[1] - HD)] <- 1
yD[all_data$Joint_Delta > (qntD[2] + HD)] <- 1
yD
all_data$Outlier_Delta <- yD

# Filter First ('REAL') data based on Asynchrony &/or Delta outliers
all_dataF <- all_data %>% filter(Outlier_Async == 0 & Outlier_Alpha == 0 & Outlier_Delta == 0) # Option filtering Aync, Alpha & Delta outliers
# first_dataF <- dyad_data %>% filter(Outlier_Delta == 0) # Option filtering only Delta outliers
all_data <- all_dataF # COMMENT OUT IF FILTERING NOT WANTED
```

### Combine the information to a combined, filtered info table (in this case no values were filtered)

```{r}
# Extract relevant info for reporting
all_info_filt <- all_data[, c('ID', 'Song', 'Artist', 'Tempo', 'IOI Entropy', 'N_Events', 'Mn_ITI', 'CV_ITI')]
colnames(all_info_filt) <- c('ID', 'Song', 'Artist', 'Tempo', 'IOI Entropy', 'N_Events', 'Mn_ITI', 'CV_ITI')

# Order rows for cleaner display
all_info_filt_order <- all_info_filt[order(all_info_filt$ID, all_info_filt$Song, all_info_filt$Artist), ]

# Format with flextable
library(flextable)
all_info_filt.ft <- flextable(all_info_filt_order)
all_info_filt.ft <- colformat_double(all_info_filt.ft, digits = 2)

# Save the table as a Word document
save_as_docx(all_info_filt.ft, path = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 1/Results/Sequence_Info_Filtered.docx")
```

### Create individual columns for each original experimental variable (Visual Contact, Leadership, and Piece)

```{r}
all_data <- all_data %>%
  mutate(
    Flipped = substr(ID, 1, 1),  # Assuming the first digit is Factor1
    MusicianA = substr(ID, 2, 2),  # Second digit for Factor2
    MusicianB = substr(ID, 3, 3))   # Third digit for Factor3
```

### Make sure all the necessary values are numeric

```{r}
# Make sure variables are numeric
all_data <- all_data %>%
  mutate(across(c(DV_Async, Mn_ITI, SD_ITI, CV_ITI, Adapt_Alpha, Adapt_Beta, Adapt_Tn, Adapt_Mn, Adapt_LLE,
                  Joint_Beta, Joint_Delta, Joint_Gamma, Joint_Tn, Joint_LLE, N_Events), as.numeric))
```

### Get means for plotting original data

```{r}
# Averages across original & reverse (target & reference), visual contact condition as well as Pair
all_data_pairs <- all_data %>% group_by(Song, Artist, MusicianA, MusicianB) %>% summarise_at(vars(DV_Async, Mn_ITI,SD_ITI,CV_ITI,
                                                                             Adapt_Alpha,Adapt_Beta,Adapt_Tn,Adapt_Mn,Adapt_LLE, Joint_Beta,Joint_Delta,Joint_Gamma,Joint_Tn,Joint_LLE, N_Events), mean, na.rm = TRUE)

all_data_pairs <- all_data_pairs %>%
  mutate(Pair_Label = case_when(
    (MusicianA == 1 & MusicianB == 2) ~ "12",
    (MusicianA == 1 & MusicianB == 3) ~ "13",
    (MusicianA == 2 & MusicianB == 3) ~ "23",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(Pair_Label))

# Averages across original & reverse (target & reference) 
all_data_group <- all_data %>% group_by(Song, Artist) %>% summarise_at(vars(DV_Async, Mn_ITI,SD_ITI,CV_ITI,
                                                                                            Adapt_Alpha,Adapt_Beta,Adapt_Tn,Adapt_Mn,Adapt_LLE, Joint_Beta,Joint_Delta,Joint_Gamma,Joint_Tn,Joint_LLE, N_Events), mean, na.rm = TRUE)

```

### Plot asynchronies

```{r}
# Set theme
raincloud_theme = theme(
  panel.background = element_rect(fill = NA, color = "black", linewidth = 1), # Change size to linewidth
  text = element_text(size = 24),
  axis.title.x = element_text(size = 24, vjust = 0, margin = margin(b = 5, t = 5)),
  axis.title.y = element_text(size = 24, vjust = 2, margin = margin(l = 5, r = 3)),
  axis.text = element_text(size = 20, color = 'black'),
  #axis.text.x = element_text(angle = 45, vjust = 0.5),
  legend.title = element_text(size = 20),
  legend.text = element_text(size = 20),
  legend.position = "top",
  plot.title = element_text(lineheight = .8, face = "bold", size = 24),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  axis.line.x = element_line(colour = 'black', linewidth = 0.5, linetype = 'solid'), # Change size to linewidth
  axis.line.y = element_line(colour = 'black', linewidth = 0.5, linetype = 'solid'), # Change size to linewidth
  plot.margin = margin(12, 6, 6, 6, "pt")) # t, r, b, l - For Portrait
  
# Asynchrony plot for all trials
Pair_plot <- all_data_pairs %>%  # Replace with your actual data frame name
  mutate(Pair_Label = factor(Pair_Label, levels = c("12", "13", "23"))) %>%
  ggplot(aes(y = DV_Async, x = Pair_Label, fill = Pair_Label)) +
  geom_flat_violin(position = position_nudge(.15), alpha = .8) +
  geom_point(position = position_jitter(.05), shape = 21, size = 4, color = "black", alpha = 0.5) +
  geom_boxplot(position = position_nudge(-.2), width = .2, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) +
  scale_fill_manual(values = rep('darkgrey', 3)) +
  labs(x = "Performance Pair", y = "Asynchrony (s)") +
  scale_x_discrete(labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  ggtitle("Pair-Based Asynchrony") +
  theme_bw() +
  raincloud_theme + 
  theme(legend.position = "none")

Group_plot <- all_data_group %>%
  ggplot(aes(x = "", y = DV_Async)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'darkgrey', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'darkgrey', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'darkgrey', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Asynchrony (Beats)",
    title = "Group Asynchrony"
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

#Combine both plots for output
Asynchrony_Plot <- ggarrange(Pair_plot, Group_plot, 
                                  labels = c("A", "B"),
                                  label.x = c(-.001, -.001),
                                  label.y = c(1.02, 1.02),
                                  font.label=list(color="black",size=20),
                                  ncol = 1, nrow = 2)
Asynchrony_Plot
```

# TEMPO NORMALIZED ASYNCHRONIES
### SD of signed asynchronies

```{r}
Norm_DV_Async <- as.symbol('Norm_SD_Signed_Async')
```

### Extract Pair, Code, \`Lead/Phrase, N_Events, Mean ITI, & CV ITI info for each sequence (for reporting in table) for both conditions

```{r}
norm_all_data <- read_excel("C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/ThesisADAM_boundedresults.xlsx")
norm_all_data <- norm_all_data %>% mutate_all(~ifelse(is.nan(.), NA, .)) # Convert NaNs to NA
norm_all_data$Norm_DV_Async <- norm_all_data[[Norm_DV_Async]]

# Extract Pair, Code, `Lead/Phrase, N_Events, Mean ITI, & CV ITI info for each sequence (for reporting in table)
norm_all_info <- norm_all_data[1:(nrow(norm_all_data)), c('ID', 'Song', 'Artist', 'Tempo', 'IOI Entropy', 'N_Events', 'Mn_ITI', 'CV_ITI')]
colnames(norm_all_info) <- c('ID', 'Song', 'Artist', 'Tempo', 'IOI Entropy', 'N events', 'Mean Interval (s)', 'CV Interval (prop.)')

```

### Make table

```{r}
# Order the table
norm_all_info_order <- norm_all_info[order(norm_all_info$ID, norm_all_info$Song, norm_all_info$Artist), ]

# Format as a flextable
norm_all_info.ft <- flextable(norm_all_info_order)
norm_all_info.ft <- colformat_double(norm_all_info.ft, digits = 2)

# Export to Word document
save_as_docx(norm_all_info.ft, path = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 1/Results/Norm_Sequence_Info_Unfiltered.docx")
```

### Filter information table for each section for outliers

```{r}
# FILTER REAL CONDITION
# Add column to indicate outliers based on asynchronies
norm_all_data$Outlier_Async <- 0
outCrit <- 3 # Set outlier criterion: How many times IQR

norm_all_data$Norm_DV_Async <- as.numeric(as.character(norm_all_data$Norm_DV_Async))
qnt <- quantile(norm_all_data$Norm_DV_Async, probs=c(.25, .75), na.rm = TRUE)
H <- outCrit * IQR(norm_all_data$Norm_DV_Async, na.rm = TRUE)
y <- norm_all_data$Outlier_Async
y[norm_all_data$Norm_DV_Async < (qnt[1] - H)] <- 1
y[norm_all_data$Norm_DV_Async > (qnt[2] + H)] <- 1
y
norm_all_data$Outlier_Async <- y

# Add column to indicate outliers based on temporal prediction (delta)
norm_all_data$Outlier_Alpha <- 0

norm_all_data$Adapt_Alpha <- as.numeric(as.character(norm_all_data$Adapt_Alpha))
qntA <- quantile(norm_all_data$Adapt_Alpha, probs=c(.25, .75), na.rm = TRUE)
HA <- outCrit * IQR(norm_all_data$Adapt_Alpha, na.rm = TRUE)
yA <- norm_all_data$Outlier_Alpha
yA[norm_all_data$Adapt_Alpha < (qntA[1] - HA)] <- 1
yA[norm_all_data$Adapt_Alpha > (qntA[2] + HA)] <- 1
yA
norm_all_data$Outlier_Alpha <- yA

# Add column to indicate outliers based on temporal prediction (delta)
norm_all_data$Outlier_Delta <- 0

norm_all_data$Joint_Delta <- as.numeric(as.character(norm_all_data$Joint_Delta))
qntD <- quantile(norm_all_data$Joint_Delta, probs=c(.25, .75), na.rm = TRUE)
HD <- outCrit * IQR(norm_all_data$Joint_Delta, na.rm = TRUE)
yD <- norm_all_data$Outlier_Delta
yD[norm_all_data$Joint_Delta < (qntD[1] - HD)] <- 1
yD[norm_all_data$Joint_Delta > (qntD[2] + HD)] <- 1
yD
norm_all_data$Outlier_Delta <- yD

# Filter First ('REAL') data based on Asynchrony &/or Delta outliers
norm_all_dataF <- norm_all_data %>% filter(Outlier_Async == 0 & Outlier_Alpha == 0 & Outlier_Delta == 0) # Option filtering Aync, Alpha & Delta outliers
# first_dataF <- dyad_data %>% filter(Outlier_Delta == 0) # Option filtering only Delta outliers
norm_all_data <- norm_all_dataF # COMMENT OUT IF FILTERING NOT WANTED
```

### Combine the information to a combined, filtered info table (in this case no values were filtered)

```{r}
# Extract relevant info for reporting
norm_all_info_filt <- norm_all_data[, c('ID', 'Song', 'Artist', 'Tempo', 'IOI Entropy', 'N_Events', 'Mn_ITI', 'CV_ITI')]
colnames(norm_all_info_filt) <- c('ID', 'Song', 'Artist', 'Tempo', 'IOI Entropy', 'N_Events', 'Mn_ITI', 'CV_ITI')

# Order rows for cleaner display
norm_all_info_filt_order <- norm_all_info_filt[order(norm_all_info_filt$ID, norm_all_info_filt$Song, norm_all_info_filt$Artist), ]

# Format with flextable
library(flextable)
norm_all_info_filt.ft <- flextable(norm_all_info_filt_order)
norm_all_info_filt.ft <- colformat_double(norm_all_info_filt.ft, digits = 2)

# Save the table as a Word document
save_as_docx(all_info_filt.ft, path = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 1/Results/Norm_Sequence_Info_Filtered.docx")
```

### Create individual columns for each original experimental variable (Visual Contact, Leadership, and Piece)

```{r}
norm_all_data <- norm_all_data %>%
  mutate(
    Flipped = substr(ID, 1, 1),  # Assuming the first digit is Factor1
    MusicianA = substr(ID, 2, 2),  # Second digit for Factor2
    MusicianB = substr(ID, 3, 3))   # Third digit for Factor3
```

### Make sure all the necessary values are numeric

```{r}
# Make sure variables are numeric
norm_all_data <- norm_all_data %>%
  mutate(across(c(Norm_DV_Async, Mn_ITI, SD_ITI, CV_ITI, Adapt_Alpha, Adapt_Beta, Adapt_Tn, Adapt_Mn, Adapt_LLE,
                  Joint_Beta, Joint_Delta, Joint_Gamma, Joint_Tn, Joint_LLE, N_Events), as.numeric))
```

### Get means for plotting original data

```{r}
# Averages across original & reverse (target & reference), visual contact condition as well as Pair
norm_all_data_pairs <- norm_all_data %>% group_by(Song, Artist, MusicianA, MusicianB) %>% summarise_at(vars(Norm_DV_Async, Mn_ITI,SD_ITI,CV_ITI,
                                                                             Adapt_Alpha,Adapt_Beta,Adapt_Tn,Adapt_Mn,Adapt_LLE, Joint_Beta,Joint_Delta,Joint_Gamma,Joint_Tn,Joint_LLE, N_Events), mean, na.rm = TRUE)

norm_all_data_pairs <- norm_all_data_pairs %>%
  mutate(Pair_Label = case_when(
    (MusicianA == 1 & MusicianB == 2) ~ "12",
    (MusicianA == 1 & MusicianB == 3) ~ "13",
    (MusicianA == 2 & MusicianB == 3) ~ "23",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(Pair_Label))

# Averages across original & reverse (target & reference) 
norm_all_data_group <- norm_all_data %>% group_by(Song, Artist) %>% summarise_at(vars(Norm_DV_Async, Mn_ITI,SD_ITI,CV_ITI,
                                                                                            Adapt_Alpha,Adapt_Beta,Adapt_Tn,Adapt_Mn,Adapt_LLE, Joint_Beta,Joint_Delta,Joint_Gamma,Joint_Tn,Joint_LLE, N_Events), mean, na.rm = TRUE)

```

### Plot asynchronies in 2x2 design (pairs for first and second eight x visual contact)

```{r}
# Set theme
raincloud_theme = theme(
  panel.background = element_rect(fill = NA, color = "black", linewidth = 1), # Change size to linewidth
  text = element_text(size = 24),
  axis.title.x = element_text(size = 24, vjust = 0, margin = margin(b = 5, t = 5)),
  axis.title.y = element_text(size = 24, vjust = 2, margin = margin(l = 5, r = 3)),
  axis.text = element_text(size = 20, color = 'black'),
  #axis.text.x = element_text(angle = 45, vjust = 0.5),
  legend.title = element_text(size = 20),
  legend.text = element_text(size = 20),
  legend.position = "top",
  plot.title = element_text(lineheight = .8, face = "bold", size = 24),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  axis.line.x = element_line(colour = 'black', linewidth = 0.5, linetype = 'solid'), # Change size to linewidth
  axis.line.y = element_line(colour = 'black', linewidth = 0.5, linetype = 'solid'), # Change size to linewidth
  plot.margin = margin(12, 6, 6, 6, "pt")) # t, r, b, l - For Portrait
  
# Asynchrony plot for all trials
Norm_Pair_plot <- norm_all_data_pairs %>%  # Replace with your actual data frame name
  mutate(Pair_Label = factor(Pair_Label, levels = c("12", "13", "23"))) %>%
  ggplot(aes(y = Norm_DV_Async, x = Pair_Label, fill = Pair_Label)) +
  geom_flat_violin(position = position_nudge(.15), alpha = .8) +
  geom_point(position = position_jitter(.05), shape = 21, size = 4, color = "black", alpha = 0.5) +
  geom_boxplot(position = position_nudge(-.2), width = .2, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) +
  scale_fill_manual(values = rep('darkgrey', 3)) +
  labs(x = "Performance Pair", y = "Asynchrony (s)") +
  scale_x_discrete(labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  ggtitle("Pair-Based Asynchrony - Tempo Normalized") +
  theme_bw() +
  raincloud_theme + 
  theme(legend.position = "none")

Norm_Group_plot <- norm_all_data_group %>%
  ggplot(aes(x = "", y = Norm_DV_Async)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'darkgrey', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'darkgrey', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'darkgrey', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Asynchrony (s)",
    title = "Group Asynchrony - Tempo Normalized"
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

#Combine both plots for output
Norm_Asynchrony_Plot <- ggarrange(Norm_Pair_plot, Norm_Group_plot, 
                                  labels = c("A", "B"),
                                  label.x = c(-.001, -.001),
                                  label.y = c(1.02, 1.02),
                                  font.label=list(color="black",size=20),
                                  ncol = 1, nrow = 2)
Norm_Asynchrony_Plot
```

```{r}
set.seed(2001)
#Check normality
ntesta1 <- norm_all_data %>% shapiro_test(Norm_DV_Async)
ntesta1

#Determine best method for transformation
bestNormalize(norm_all_data$Norm_DV_Async) #Order Norm

#Complete transforation and check normality for improvement
Norm_DV_Async_ON <- bestNormalize(norm_all_data$Norm_DV_Async)
norm_all_data$Norm_DV_Async_ON <- predict(Norm_DV_Async_ON, norm_all_data$Norm_DV_Async)
ntestLLE <- norm_all_data %>% shapiro_test(Norm_DV_Async_ON) 
ntestLLE
```

#  TRANSFORMED TEMPO NORMALIZED ASYNCHRONIES
### Filter information table for each section for outliers

```{r}
# FILTER REAL CONDITION
# Add column to indicate outliers based on asynchronies
norm_all_data$Outlier_Async <- 0
outCrit <- 3 # Set outlier criterion: How many times IQR

norm_all_data$Norm_DV_Async_ON <- as.numeric(as.character(norm_all_data$Norm_DV_Async_ON))
qnt <- quantile(norm_all_data$Norm_DV_Async_ON, probs=c(.25, .75), na.rm = TRUE)
H <- outCrit * IQR(norm_all_data$Norm_DV_Async_ON, na.rm = TRUE)
y <- norm_all_data$Outlier_Async
y[norm_all_data$Norm_DV_Async_ON < (qnt[1] - H)] <- 1
y[norm_all_data$Norm_DV_Async_ON > (qnt[2] + H)] <- 1
y
norm_all_data$Outlier_Async <- y

# Add column to indicate outliers based on temporal prediction (delta)
norm_all_data$Outlier_Alpha <- 0

norm_all_data$Adapt_Alpha <- as.numeric(as.character(norm_all_data$Adapt_Alpha))
qntA <- quantile(norm_all_data$Adapt_Alpha, probs=c(.25, .75), na.rm = TRUE)
HA <- outCrit * IQR(norm_all_data$Adapt_Alpha, na.rm = TRUE)
yA <- norm_all_data$Outlier_Alpha
yA[norm_all_data$Adapt_Alpha < (qntA[1] - HA)] <- 1
yA[norm_all_data$Adapt_Alpha > (qntA[2] + HA)] <- 1
yA
norm_all_data$Outlier_Alpha <- yA

# Add column to indicate outliers based on temporal prediction (delta)
norm_all_data$Outlier_Delta <- 0

norm_all_data$Joint_Delta <- as.numeric(as.character(norm_all_data$Joint_Delta))
qntD <- quantile(norm_all_data$Joint_Delta, probs=c(.25, .75), na.rm = TRUE)
HD <- outCrit * IQR(norm_all_data$Joint_Delta, na.rm = TRUE)
yD <- norm_all_data$Outlier_Delta
yD[norm_all_data$Joint_Delta < (qntD[1] - HD)] <- 1
yD[norm_all_data$Joint_Delta > (qntD[2] + HD)] <- 1
yD
norm_all_data$Outlier_Delta <- yD

# Filter First ('REAL') data based on Asynchrony &/or Delta outliers
norm_all_dataF <- norm_all_data %>% filter(Outlier_Async == 0 & Outlier_Alpha == 0 & Outlier_Delta == 0) # Option filtering Aync, Alpha & Delta outliers
# first_dataF <- dyad_data %>% filter(Outlier_Delta == 0) # Option filtering only Delta outliers
norm_all_data <- norm_all_dataF # COMMENT OUT IF FILTERING NOT WANTED
```

### Make sure all the necessary values are numeric

```{r}
# Make sure variables are numeric
norm_all_data <- norm_all_data %>%
  mutate(across(c(Norm_DV_Async_ON, Mn_ITI, SD_ITI, CV_ITI, Adapt_Alpha, Adapt_Beta, Adapt_Tn, Adapt_Mn, Adapt_LLE,
                  Joint_Beta, Joint_Delta, Joint_Gamma, Joint_Tn, Joint_LLE, N_Events), as.numeric))
```

### Get means for plotting original data

```{r}
# Averages across original & reverse (target & reference), visual contact condition as well as Pair
norm_all_data_pairs <- norm_all_data %>% group_by(Song, Artist, MusicianA, MusicianB) %>% summarise_at(vars(Norm_DV_Async_ON, Mn_ITI,SD_ITI,CV_ITI,
                                                                             Adapt_Alpha,Adapt_Beta,Adapt_Tn,Adapt_Mn,Adapt_LLE, Joint_Beta,Joint_Delta,Joint_Gamma,Joint_Tn,Joint_LLE, N_Events), mean, na.rm = TRUE)

norm_all_data_pairs <- norm_all_data_pairs %>%
  mutate(Pair_Label = case_when(
    (MusicianA == 1 & MusicianB == 2) ~ "12",
    (MusicianA == 1 & MusicianB == 3) ~ "13",
    (MusicianA == 2 & MusicianB == 3) ~ "23",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(Pair_Label))

# Averages across original & reverse (target & reference) 
norm_all_data_group <- norm_all_data %>% group_by(Song, Artist) %>% summarise_at(vars(Norm_DV_Async_ON, Mn_ITI,SD_ITI,CV_ITI,
                                                                                            Adapt_Alpha,Adapt_Beta,Adapt_Tn,Adapt_Mn,Adapt_LLE, Joint_Beta,Joint_Delta,Joint_Gamma,Joint_Tn,Joint_LLE, N_Events), mean, na.rm = TRUE)

```

### Plot asynchronies in 2x2 design (pairs for first and second eight x visual contact)

```{r}
# Set theme
raincloud_theme = theme(
  panel.background = element_rect(fill = NA, color = "black", linewidth = 1), # Change size to linewidth
  text = element_text(size = 24),
  axis.title.x = element_text(size = 24, vjust = 0, margin = margin(b = 5, t = 5)),
  axis.title.y = element_text(size = 24, vjust = 2, margin = margin(l = 5, r = 3)),
  axis.text = element_text(size = 20, color = 'black'),
  #axis.text.x = element_text(angle = 45, vjust = 0.5),
  legend.title = element_text(size = 20),
  legend.text = element_text(size = 20),
  legend.position = "top",
  plot.title = element_text(lineheight = .8, face = "bold", size = 24),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  axis.line.x = element_line(colour = 'black', linewidth = 0.5, linetype = 'solid'), # Change size to linewidth
  axis.line.y = element_line(colour = 'black', linewidth = 0.5, linetype = 'solid'), # Change size to linewidth
  plot.margin = margin(12, 6, 6, 6, "pt")) # t, r, b, l - For Portrait
  
# Asynchrony plot for all trials
Norm_Pair_plot <- norm_all_data_pairs %>%  # Replace with your actual data frame name
  mutate(Pair_Label = factor(Pair_Label, levels = c("12", "13", "23"))) %>%
  ggplot(aes(y = Norm_DV_Async_ON, x = Pair_Label, fill = Pair_Label)) +
  geom_flat_violin(position = position_nudge(.15), alpha = .8) +
  geom_point(position = position_jitter(.05), shape = 21, size = 4, color = "black", alpha = 0.5) +
  geom_boxplot(position = position_nudge(-.2), width = .2, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) +
  scale_fill_manual(values = rep('darkgrey', 3)) +
  labs(x = "Performance Pair", y = "Asynchrony (OrderNorm)") +
  scale_x_discrete(labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  ggtitle("Pair-Based Asynchrony - Normalized & Transformed") +
  theme_bw() +
  raincloud_theme + 
  theme(legend.position = "none")

Norm_Group_plot <- norm_all_data_group %>%
  ggplot(aes(x = "", y = Norm_DV_Async_ON)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'darkgrey', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'darkgrey', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'darkgrey', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Asynchrony (OrderNorm)",
    title = "Group Asynchrony - Normalized & Transformed"
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

#Combine both plots for output
Norm_Asynchrony_Plot <- ggarrange(Norm_Pair_plot, Norm_Group_plot, 
                                  labels = c("A", "B"),
                                  label.x = c(-.001, -.001),
                                  label.y = c(1.02, 1.02),
                                  font.label=list(color="black",size=20),
                                  ncol = 1, nrow = 2)
Norm_Asynchrony_Plot
```
