---
title: "Thesis ADAM Analysis 2"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

# LMERs for Asynchronies

ADAM model parameter estimates were computed in Matlab script:

ThesisADAM_boundedresults.m Output is one file which includes participant and condition identifiers, a
range of performance measures, and parameter estimates for the
'Adaptation-only' and 'Full' versions of ADAM. Log-likelihood estimates
are also included for each model version, indicating quality of model
fit to data (higher values [less -vs/more +ve] mean better fit)

Adaptation-only version includes estimates of: 
- Phase Correction ('Adapt_Alpha') 
- Period Correction ('Adapt_Beta') 
- Timekeeper Noise ('Adapt_Tn') 
- Motor Noise ('Adapt_Mn')

Joint version of ADAM includes estimates of: 
- Period correction ('Joint_Beta') 
- Temporal Prediction ('Joint_Delta') 
- Anticipatory Error Correction ('Joint_Gamma') 
- Timekeeper Noise ('Joint_Tn')

Note that the ADAM parameter estimation procedure is run twice per data
set with TARGET musician (the one for which parameters are being
estimated) and REFERENCE musician (the one for which parameters are NOT
being estimated) swapped so estimates are given for each musician.

### Set directory where to read and write files

```{r}
setwd("C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis") # NEED TO SET TO CURRENT PATH
```

### Load libraries

```{r}
library(bestNormalize)
library(caret)
library(dplyr)
library(emmeans)
library(flextable)
library(ggeffects)
library(ggplot2)
library(ggpp) # for jitternudge [not currently used]
library(ggpubr)
library(ggsci) # For Raincloud plots
library(grid)
library(gridExtra)
library(gtools)
library(huxtable)
library(broom.mixed)
library(lme4) # For lmer
library(lmerTest) # Alternative for lmer that gives p-values/asterisks. Automatically updates output of lmer (just load here, no need to call below) 
library(reshape2)
library(rstatix)
library(stats) # For confint
library(tidyr)
library(tidyverse)
library(readxl)
library(CRSSIO) # This has additional custom editing features for boxplot
library(interactions)
```

## Statistical Tests of Asynchrony

### Remove NAN's for transformation

```{r}
print("Rows removed due to NaN in DV_Async (Section and Pair):")
all_data_pairs %>%
  filter(is.na(DV_Async)) %>%
  mutate(removed_info = paste(Song, Artist, Pair_Label)) %>%
  pull(removed_info) %>%
  print()
# Remove rows with NaN in DV_Async and proceed with the analysis
all_data_pairs <- all_data_pairs %>% filter(!is.na(DV_Async))
```

### Check the dataset for normality and transform if not normal

```{r}
#Check normality
ntesta1 <- all_data %>% shapiro_test(DV_Async)
ntesta1

#Determine best method for transformation
bestNormalize(all_data$DV_Async) #Order Norm

#Complete transforation and check normality for improvement
DV_Async_ON <- bestNormalize(all_data$DV_Async)
all_data$DV_Async_ON <- predict(DV_Async_ON, all_data$DV_Async)
ntestLLE <- all_data %>% shapiro_test(DV_Async_ON) 
ntestLLE
```


### Ensure that all relevant columns are factors before LMER

```{r}
all_data <- all_data %>%
  mutate(Pair_Label = case_when(
    (MusicianA == 1 & MusicianB == 2) ~ "12",
    (MusicianA == 1 & MusicianB == 3) ~ "13",
    (MusicianA == 2 & MusicianB == 3) ~ "23",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(Pair_Label))
all_data$Pair_Label <- factor(all_data$Pair_Label, levels = c("12", "13","23"))
names(all_data)[names(all_data) == "IOI Entropy"] <- "IOI_Entropy"
all_data$IOI_Entropy_z <- scale(all_data$IOI_Entropy)
all_data$Tempo_z <- scale(all_data$Tempo)

all_data <- all_data %>%
  mutate(Pair_Label = as.character(Pair_Label),  # Convert to character to handle numeric changes
         Pair_Label = ifelse(Flipped == 2, 
                              case_when(
                                Pair_Label == "12" ~ "21",
                                Pair_Label == "13" ~ "31",
                                Pair_Label == "23" ~ "32",
                                TRUE ~ Pair_Label  # Keep other values unchanged
                              ),
                              Pair_Label))

# Print the updated columns to check
print(all_data %>% select(ID, Pair_Label, Flipped))
```

## Asynchrony LMER Model

### Full Model

```{r}
Asynchrony.lmer <- lmer(DV_Async_ON ~ Pair_Label * IOI_Entropy_z * Tempo_z + (1 | Song) + (1 | Artist) + (1 | N_Events),
                        data = all_data, 
                        control = lmerControl(optimizer = "bobyqa"), 
                        REML = FALSE)
# Model summary
Asynchrony.lmer_output <- summary(Asynchrony.lmer)
Asynchrony.lmer_output
capture.output(Asynchrony.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/Asynchrony_LMER_output.txt") # Write output to text file

Asynchrony.ci <- confint(Asynchrony.lmer) # Doesn't work with Box-Cox transformed asynchronies
Asynchrony.ci
capture.output(Asynchrony.ci, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/Asynchrony_CI.txt")
```

### Random Model

```{r}
# Random Effects LMER model
Asynchrony_random.lmer <- lmer(DV_Async_ON ~ 1 + + (1 | Artist/Song), data = all_data, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Asynchrony_random_output <- summary(Asynchrony_random.lmer)
Asynchrony_random_output
capture.output(Asynchrony_random_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/Asynchrony_random_output.txt") # Write output to text file
```

### Compare Models

```{r}
# Compare full and reduced models 
Asynchrony_models_comparison <- anova(Asynchrony.lmer, Asynchrony_random.lmer)
Asynchrony_models_comparison
capture.output(Asynchrony_models_comparison, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/Asynchrony_comparison.txt") # Write output to text file
```

```{r}
Asynchrony.table <- huxreg(Asynchrony.lmer, Asynchrony_random.lmer, statistics = NULL, number_format = 4)
Asynchrony.table
huxtable::quick_docx(Asynchrony.table, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/Asynchrony_MEAN_table.docx") # Make Word table (not standardized coefficients)
```

```{r}
# Create a named vector for facet labels
pair_labels <- c(
  "12" = "Piano (Bass)",
  "13" = "Piano (Drums)",
  "23" = "Bass (Drums)",
  "21" = "Bass (Piano)",
  "31" = "Drums (Piano)",
  "32" = "Drums (Bass)"
)

complexity_pair_plot <- interact_plot(
  Asynchrony.lmer,
  pred = IOI_Entropy_z,
  modx = Pair_Label,
  plot.points = TRUE,
  interval = TRUE,
  point.alpha = 0.3,   # more opaque dots
  line.alpha = 1,      # fully visible lines
  linetype = "solid"   # all lines solid
) +
  labs(
    x = "Part Complexity (z)",
    y = "Individual Asynchrony (ON)",
    color = "Paired Musicians",
    fill = "Paired Musicians"
  ) +
  scale_color_manual(
    values = c(
      "12" = "#66C2A5",
      "13" = "#FC8D62",
      "23" = "#8DA0CB",
      "21" = "#E78AC3",
      "31" = "#A6D854",
      "32" = "#D73027"
    ),
    labels = pair_labels
  ) +
  scale_fill_manual(
    values = c(
      "12" = "#66C2A5",
      "13" = "#FC8D62",
      "23" = "#8DA0CB",
      "21" = "#E78AC3",
      "31" = "#A6D854",
      "32" = "#D73027"
    ),
    labels = pair_labels
  ) +
  facet_wrap(~ Pair_Label, labeller = labeller(Pair_Label = pair_labels)) +
  guides(linetype = "none") +  # removes line type legend
  theme_classic(base_size = 14) +
  theme(
    legend.position = "top",
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    axis.line = element_line(color = "black")
  )

complexity_pair_plot

```

```{r}
# Create a named vector for facet labels
pair_labels <- c(
  "12" = "Piano (Bass)",
  "13" = "Piano (Drums)",
  "23" = "Bass (Drums)",
  "21" = "Bass (Piano)",
  "31" = "Drums (Piano)",
  "32" = "Drums (Bass)"
)

tempo_pair_plot <- interact_plot(
  Asynchrony.lmer,
  pred = Tempo_z,
  modx = Pair_Label,
  plot.points = TRUE,
  interval = TRUE,
  point.alpha = 0.3,   # more opaque dots
  line.alpha = 1,      # fully visible lines
  linetype = "solid"   # all lines solid
) +
  labs(
    x = "Tempo (z)",
    y = "Individual Asynchrony (ON)",
    color = "Paired Musicians",
    fill = "Paired Musicians"
  ) +
  scale_color_manual(
    values = c(
      "12" = "#66C2A5",
      "13" = "#FC8D62",
      "23" = "#8DA0CB",
      "21" = "#E78AC3",
      "31" = "#A6D854",
      "32" = "#D73027"
    ),
    labels = pair_labels
  ) +
  scale_fill_manual(
    values = c(
      "12" = "#66C2A5",
      "13" = "#FC8D62",
      "23" = "#8DA0CB",
      "21" = "#E78AC3",
      "31" = "#A6D854",
      "32" = "#D73027"
    ),
    labels = pair_labels
  ) +
  facet_wrap(~ Pair_Label, labeller = labeller(Pair_Label = pair_labels)) +
  guides(linetype = "none") +  # removes line type legend
  theme_classic(base_size = 14) +
  theme(
    legend.position = "top",
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    axis.line = element_line(color = "black")
  )

tempo_pair_plot
```


## Group Asynch LMER

```{r}
# Filter out the flipped versions (Flipped == 1)
filtered_data <- all_data %>%
  filter(Flipped == 1)

# 1. Calculate the RMS of DV_Async_ON for each group
rms_table <- filtered_data %>%
  group_by(Song, Artist) %>%
  summarise(Group_Async_ON = sqrt(mean(DV_Async_ON^2, na.rm = TRUE)), .groups = "drop")

# 2. Calculate global IOI entropy per Song/Artist using N_Events weighting
ioi_entropy_global <- all_data %>%
  group_by(Song, Artist) %>%
  summarise(
    IOI_Entropy_Global = sum(IOI_Entropy * N_Events, na.rm = TRUE) / sum(N_Events, na.rm = TRUE),
    Total_Events = sum(N_Events, na.rm = TRUE),
    .groups = "drop"
  )

# 3. Create averaged summary of all other variables (including IOI_Entropy mean)
all_data_group <- all_data %>% 
  group_by(Song, Artist) %>% 
  summarise_at(vars(
    DV_Async, Tempo, IOI_Entropy, SD_ITI, CV_ITI,
    Adapt_Alpha_ON, Adapt_Beta_ON, Adapt_Tn_ON, Adapt_Mn_ON, Adapt_LLE,
    Joint_Beta_ON, Joint_Delta_ON, Joint_Gamma_ON, Joint_Tn_ON, Joint_LLE, N_Events
  ), mean, na.rm = TRUE)

# 4. Z-score key predictors
all_data_group$IOI_Entropy_z <- scale(all_data_group$IOI_Entropy)
all_data_group$Tempo_z <- scale(all_data_group$Tempo)

# 5. Merge in Group_Async_ON and IOI_Entropy_Global
all_data_group <- all_data_group %>%
  left_join(rms_table, by = c("Song", "Artist")) %>%
  left_join(ioi_entropy_global, by = c("Song", "Artist"))

all_data_group$IOI_Entropy_Global_z <- scale(all_data_group$IOI_Entropy_Global)
# 6. View updated summary
print(all_data_group)
```


### Full Model

```{r}
Asynchrony.lmer <- lmer(Group_Async_ON ~ IOI_Entropy_Global_z * Tempo_z + (1 | Song) + (1 | Artist) + (1 | N_Events),
                        data = all_data_group, 
                        control = lmerControl(optimizer = "bobyqa"), 
                        REML = FALSE)
# Model summary
Asynchrony.lmer_output <- summary(Asynchrony.lmer)
Asynchrony.lmer_output
capture.output(Asynchrony.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/GroupAsynchrony_LMER_output.txt") # Write output to text file

Asynchrony.ci <- confint(Asynchrony.lmer) # Doesn't work with Box-Cox transformed asynchronies
Asynchrony.ci
capture.output(Asynchrony.ci, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/GroupAsynchrony_CI.txt")
```

### Random Model

```{r}
# Random Effects LMER model
Asynchrony_random.lmer <- lmer(Group_Async_ON ~ 1 + (1 | Song) + (1 | Artist), data = all_data_group, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Asynchrony_random_output <- summary(Asynchrony_random.lmer)
Asynchrony_random_output
capture.output(Asynchrony_random_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/GroupAsynchrony_random_output.txt") # Write output to text file
```

### Compare Models

```{r}
# Compare full and reduced models 
Asynchrony_models_comparison <- anova(Asynchrony.lmer, Asynchrony_random.lmer)
Asynchrony_models_comparison
capture.output(Asynchrony_models_comparison, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/GroupAsynchrony_comparison.txt") # Write output to text file
```

```{r}
Asynchrony.table <- huxreg(Asynchrony.lmer, Asynchrony_random.lmer, statistics = NULL, number_format = 4)
Asynchrony.table
huxtable::quick_docx(Asynchrony.table, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 2/Results/GroupAsynchrony_MEAN_table.docx") # Make Word table (not standardized coefficients)
```
```{r}
library(interactions)
library(ggplot2)
interact_plot(
  Asynchrony.lmer,
  pred = IOI_Entropy_Global_z,
  modx = Tempo_z,
  plot.points = TRUE,
  interval = TRUE,
  modx.values = "plus-minus",
  colors = "Qual1",
  alpha = 0.2
) +
  labs(
    x = "Piece Complexity (z)",
    y = "Group Asynchrony (ON)",
    color = "Tempo (z)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "top",
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    panel.border = element_rect(color = "black", fill = NA, size = 1),  # Adds black border around entire panel
    axis.line = element_line(color = "black")  # Ensures axis lines are black too
  )


```

