---
title: "Thesis ADAM Analysis 3"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

# ADAM Parameter Plots

ADAM model parameter estimates were computed in Matlab script:

ThesisADAM_boundedresults.m Output is one file which includes participant and condition identifiers, a
range of performance measures, and parameter estimates for the
'Adaptation-only' and 'Full' versions of ADAM. Log-likelihood estimates
are also included for each model version, indicating quality of model
fit to data (higher values [less -vs/more +ve] mean better fit)

Adaptation-only version includes estimates of: 
- Phase Correction ('Adapt_Alpha') 
- Period Correction ('Adapt_Beta') 
- Timekeeper Noise ('Adapt_Tn') 
- Motor Noise ('Adapt_Mn')

Joint version of ADAM includes estimates of: 
- Period correction ('Joint_Beta') 
- Temporal Prediction ('Joint_Delta') 
- Anticipatory Error Correction ('Joint_Gamma') 
- Timekeeper Noise ('Joint_Tn')

Note that the ADAM parameter estimation procedure is run twice per data
set with TARGET musician (the one for which parameters are being
estimated) and REFERENCE musician (the one for which parameters are NOT
being estimated) swapped so estimates are given for each musician.

### Set directory where to read and write files

```{r}
setwd("C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis") # NEED TO SET TO CURRENT PATH
```

### Load libraries

```{r}
library(bestNormalize)
library(caret)
library(dplyr)
library(emmeans)
library(flextable)
library(ggeffects)
library(ggplot2)
library(ggpp) # for jitternudge [not currently used]
library(ggpubr)
library(ggsci) # For Raincloud plots
library(grid)
library(gridExtra)
library(gtools)
library(huxtable)
library(broom.mixed)
library(lme4) # For lmer
library(lmerTest) # Alternative for lmer that gives p-values/asterisks. Automatically updates output of lmer (just load here, no need to call below) 
library(reshape2)
library(rstatix)
library(stats) # For confint
library(tidyr)
library(tidyverse)
library(readxl)
library(CRSSIO) # This has additional custom editing features for boxplot
```

## Plot ADAM Parameter Estimates (Transformed)

### Check normality of ADAM parameters

```{r}
#ADAPT MODEL
set.seed(2001)

#Adapt Alpha (TRANSFORMED)
ntesta3 <- all_data %>% shapiro_test(Adapt_Alpha)
ntesta3
print(bestNormalize(all_data$Adapt_Alpha))
Adapt_Alpha_ON <- bestNormalize(all_data$Adapt_Alpha)
all_data$Adapt_Alpha_ON <- predict(Adapt_Alpha_ON, all_data$Adapt_Alpha)
ntestLLE <- all_data %>% shapiro_test(Adapt_Alpha_ON) 
ntestLLE

set.seed(2001)
#Adapt Beta (TRANSFORMED)
ntesta3 <- all_data %>% shapiro_test(Adapt_Beta) 
ntesta3
print(bestNormalize(all_data$Adapt_Beta))
Adapt_Beta_ON <- bestNormalize(all_data$Adapt_Beta)
all_data$Adapt_Beta_ON <- predict(Adapt_Beta_ON, all_data$Adapt_Beta)
ntestLLE <- all_data %>% shapiro_test(Adapt_Beta_ON) 
ntestLLE

set.seed(2001)
#Adapt TN (TRANSFORMED)
ntesta3 <- all_data %>% shapiro_test(Adapt_Tn) 
ntesta3
bestNormalize(all_data$Adapt_Tn)
Adapt_Tn_ON <- bestNormalize(all_data$Adapt_Tn)
all_data$Adapt_Tn_ON <- predict(Adapt_Tn_ON, all_data$Adapt_Tn)
ntestLLE <- all_data %>% shapiro_test(Adapt_Tn_ON) 
ntestLLE

set.seed(2001)
#Adapt Mn (Kept Untransformed)
ntesta3 <- all_data %>% shapiro_test(Adapt_Mn) 
ntesta3
bestNormalize(all_data$Adapt_Mn)
Adapt_Mn_ON <- bestNormalize(all_data$Adapt_Mn)
all_data$Adapt_Mn_ON <- predict(Adapt_Mn_ON, all_data$Adapt_Mn)
ntestLLE <- all_data %>% shapiro_test(Adapt_Mn_ON) 
ntestLLE

#JOINT MODEL
set.seed(2001)

#Joint Beta (TRANSFORMED)
ntesta3 <- all_data %>% shapiro_test(Joint_Beta)
ntesta3
bestNormalize(all_data$Joint_Beta)
Joint_Beta_ON <- bestNormalize(all_data$Joint_Beta)
all_data$Joint_Beta_ON <- predict(Joint_Beta_ON, all_data$Joint_Beta)
ntestLLE <- all_data %>% shapiro_test(Joint_Beta_ON) 
ntestLLE

set.seed(2001)
#Joint Delta (TRANSFORMED, still bad arguably similar)
ntesta3 <- all_data %>% shapiro_test(Joint_Delta)
ntesta3
bestNormalize(all_data$Joint_Delta)
Joint_Delta_ON <- bestNormalize(all_data$Joint_Delta)
all_data$Joint_Delta_ON <- predict(Joint_Delta_ON, all_data$Joint_Delta)
ntestLLE <- all_data %>% shapiro_test(Joint_Delta_ON) 
ntestLLE

set.seed(2001)
#Joint Gamma (TRANSFORMED, still bad arguably similar)
ntesta3 <- all_data %>% shapiro_test(Joint_Gamma)
ntesta3
bestNormalize(all_data$Joint_Gamma)
Joint_Gamma_ON <- bestNormalize(all_data$Joint_Gamma)
all_data$Joint_Gamma_ON <- predict(Joint_Gamma_ON, all_data$Joint_Gamma)
ntestLLE <- all_data %>% shapiro_test(Joint_Gamma_ON) 
ntestLLE

set.seed(2001)
#Joint TN (TRANSFORMED, still not amazing)
ntesta3 <- all_data %>% shapiro_test(Joint_Tn)
ntesta3
bestNormalize(all_data$Joint_Tn)
Joint_Tn_ON <- bestNormalize(all_data$Joint_Tn)
all_data$Joint_Tn_ON <- predict(Joint_Tn_ON, all_data$Joint_Tn)
ntestLLE <- all_data %>% shapiro_test(Joint_Tn_ON) 
ntestLLE
```

### Define plot theme

```{r}
adam_plot_specs <- theme(panel.background = element_rect(fill = NA, color = "black", size = 1),
                                        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
                                        plot.title = element_text(color="black", size=24, face="bold"),
                                        axis.title = element_text(color = "black", size = 15), # size = 22
                                        axis.title.y = element_text(margin = margin(r = 5)), # r = 6
                                        axis.text = element_text(color = "black", size = 15), #18
                                        axis.title.x = element_text(margin = margin(t = 6)), # t = 10
                                        legend.title = element_text(color="black", size = 15), # size = 18
                                        legend.text = element_text(color="black", size = 14), # size = 16
                                        legend.key = ggplot2::element_rect(fill = NA, colour = NA),
                                        #legend.position = c(.2, .8)) # c(.8, .8)
                                        legend.position = "top",
                                        legend.box.spacing = unit(1, "pt"),
                                        #plot.margin = margin(6,6,6,6, "pt")) # t, r, b, l
                                        plot.margin = margin(28,6,6,6, "pt")) # t, r, b, l - For Portrait
#plot.margin = margin(28,9,6,9, "pt")) # t, r, b, l - For Landscape
```

### Define split Adaptation Only plots

```{r}

all_data <- all_data %>%
  mutate(Musicians_Present = case_when(
    (MusicianA == 1 & MusicianB == 2) ~ "12",
    (MusicianA == 1 & MusicianB == 3) ~ "13",
    (MusicianA == 2 & MusicianB == 3) ~ "23",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(Musicians_Present))

Adapt_Alpha_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Adapt_Alpha_ON, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Adapt_Alpha_ON, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Adapt_Alpha_ON, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightcoral', 'red','darkred')) +
  labs(x="Pair", y = "Phase Correction", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none") 

#Adapt_Alpha_plot
#ggsave("Adapt_Alpha_plot.png", dpi=600)


Adapt_Beta_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Adapt_Beta_ON, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Adapt_Beta_ON, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Adapt_Beta_ON, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightsalmon', 'orange','darkorange')) +
  labs(x="Pair", y = "Period Correction", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none")

#Adapt_Beta_plot
#ggsave("Adapt_Beta_plot.png", dpi=600)


Adapt_Tn_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Adapt_Tn_ON, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Adapt_Tn_ON, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Adapt_Tn_ON, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightgrey','darkgrey','black')) +
  labs(x="Pair", y = "Period Correction", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none")

#Adapt_Tn_plot
#ggsave("Adapt_Tn_plot.png", dpi=600)

Adapt_Mn_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Adapt_Mn_ON, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Adapt_Mn_ON, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Adapt_Mn_ON, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightgrey','darkgrey','black')) +
  labs(x="Pair", y = "Period Correction", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none")

#Adapt_Mn_plot
#ggsave("Adapt_Mn_plot.png", dpi=600)

# Adaptation only plot
ADAM_Adapt_Plot <- ggarrange(Adapt_Alpha_plot, Adapt_Beta_plot, 
                             Adapt_Tn_plot, Adapt_Mn_plot,  
                             labels = c("A", "B", "C", "D"),
                             label.x = c(-.001, -.001, -.001, -.001),
                             label.y = c(1.03, 1.03, 1.03, 1.03),
                             font.label=list(color="black",size=24),
                             ncol = 1, nrow = 4
)
ADAM_Adapt_Plot
ADAM_Adapt_Plot <- ADAM_Adapt_Plot %>% annotate_figure(top = text_grob("Adaptation Only Model", color = "Black", face = "bold", size = 24))
ADAM_Adapt_Plot
```

### Define split Joint Only plots

```{r}
Joint_Beta_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Joint_Beta_ON, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Joint_Beta_ON, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Joint_Beta_ON, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightsalmon', 'orange','darkorange')) +
  labs(x="Pair", y = "Period Correction", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none") 


Joint_Delta_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Joint_Delta_ON, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Joint_Delta_ON, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Joint_Delta_ON, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightblue','blue','royalblue')) +
  labs(x="Pair", y = "Temporal Prediction", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none")


Joint_Gamma_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Joint_Gamma_ON, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Joint_Gamma_ON, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Joint_Gamma_ON, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightgreen','darkgreen','seagreen')) +
  labs(x="Pair", y = "Anticipatory Correction", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none")

Joint_Tn_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Joint_Tn_ON, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Joint_Tn_ON, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Joint_Tn_ON, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightgrey','darkgrey','black')) +
  labs(x="Pair", y = "Timekeeper Noise", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none")

# Adaptation only plot
ADAM_Joint_Plot <- ggarrange(Joint_Beta_plot, Joint_Delta_plot, 
                             Joint_Gamma_plot, Joint_Tn_plot,  
                             labels = c("A", "B", "C", "D"),
                             label.x = c(-.001, -.001, -.001, -.001),
                             label.y = c(1.03, 1.03, 1.03, 1.03),
                             font.label=list(color="black",size=24),
                             ncol = 1, nrow = 4
)
ADAM_Joint_Plot
ADAM_Joint_Plot <- ADAM_Joint_Plot %>% annotate_figure(top = text_grob("Joint Model", color = "Black", face = "bold", size = 24))
ADAM_Joint_Plot
```

### Combine Plots

```{r}
ADAM_Split_Full_Plot <- ggarrange(ADAM_Adapt_Plot, ADAM_Joint_Plot, ncol = 2, nrow = 1)
ADAM_Split_Full_Plot
ADAM_Split_Full_Plot <- ADAM_Split_Full_Plot %>% annotate_figure(top = text_grob("ADAM Parameters - Pairwise", color = "Black", face = "bold", size = 40))
ADAM_Split_Full_Plot
```

# PLOT NOT PAIRWISE

```{r}
Adapt_Alpha_plot <- all_data %>%
  ggplot(aes(x = "", y = Adapt_Alpha_ON)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'red', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'red', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'red', alpha = 0.5) +
  labs(
    x = NULL,
    y = "" #Phase Correction
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Adapt_Beta_plot <- all_data %>%
  ggplot(aes(x = "", y = Adapt_Beta_ON)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'orange', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'orange', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'orange', alpha = 0.5) +
  labs(
    x = NULL,
    y = "" #Period Correction
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Adapt_Tn_plot <- all_data %>%
  ggplot(aes(x = "", y = Adapt_Tn_ON)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'grey', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'grey', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'grey', alpha = 0.5) +
  labs(
    x = NULL,
    y = "" #Timekeeper Noise
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Adapt_Mn_plot <- all_data %>%
  ggplot(aes(x = "", y = Adapt_Mn_ON)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'grey', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'grey', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'grey', alpha = 0.5) +
  labs(
    x = NULL,
    y = "" #Motor Noise
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


# Adaptation only plot
ADAM_Adapt_Plot_Com <- ggarrange(Adapt_Alpha_plot, Adapt_Beta_plot, 
                             Adapt_Tn_plot, Adapt_Mn_plot,  
                             labels = c("A", "B", "C", "D"),
                             label.x = c(-.001, -.001, -.001, -.001),
                             label.y = c(1.03, 1.03, 1.03, 1.03),
                             font.label=list(color="black",size=24),
                             ncol = 1, nrow = 4
)
ADAM_Adapt_Plot_Com
ADAM_Adapt_Plot_Com <- ADAM_Adapt_Plot_Com %>% annotate_figure(top = text_grob("Adaptation Only Model", color = "Black", face = "bold", size = 24))
ADAM_Adapt_Plot_Com
```

```{r}
Joint_Beta_plot <- all_data %>%
  ggplot(aes(x = "", y = Joint_Beta_ON)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'orange', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'orange', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'orange', alpha = 0.5) +
  labs(
    x = NULL,
    y = "" #Period Correction
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Joint_Delta_plot <- all_data %>%
  ggplot(aes(x = "", y = Joint_Delta_ON)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'blue', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'blue', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'blue', alpha = 0.5) +
  labs(
    x = NULL,
    y = "" #Temporal Prediction
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Joint_Gamma_plot <- all_data %>%
  ggplot(aes(x = "", y = Joint_Gamma_ON)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'darkgreen', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'darkgreen', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'darkgreen', alpha = 0.5) +
  labs(
    x = NULL,
    y = "" #Anticipatory Correction
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Joint_Tn_plot <- all_data %>%
  ggplot(aes(x = "", y = Joint_Tn_ON)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'grey', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'grey', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'grey', alpha = 0.5) +
  labs(
    x = NULL,
    y = "" #Timekeeper Noise
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


# Adaptation only plot
ADAM_Joint_Plot_Com <- ggarrange(Joint_Beta_plot, Joint_Delta_plot, 
                             Joint_Gamma_plot, Joint_Tn_plot,  
                             labels = c("A", "B", "C", "D"),
                             label.x = c(-.001, -.001, -.001, -.001),
                             label.y = c(1.03, 1.03, 1.03, 1.03),
                             font.label=list(color="black",size=24),
                             ncol = 1, nrow = 4
)
ADAM_Joint_Plot_Com
ADAM_Joint_Plot_Com <- ADAM_Joint_Plot_Com %>% annotate_figure(top = text_grob("Joint Model", color = "Black", face = "bold", size = 24))
ADAM_Joint_Plot_Com
```
### Combine Plots

```{r}
ADAM_Full_Plot <- ggarrange(ADAM_Adapt_Plot_Com, ADAM_Joint_Plot_Com, ncol = 2, nrow = 1)
ADAM_Full_Plot
ADAM_Full_Plot <- ADAM_Full_Plot %>% annotate_figure(top = text_grob("ADAM Parameters", color = "Black", face = "bold", size = 40))
ADAM_Full_Plot
```

```{r}
ADAM_ComAdapt_Plot <- ggarrange(ADAM_Adapt_Plot, ADAM_Adapt_Plot_Com, ncol = 2, nrow = 1)
ADAM_ComAdapt_Plot
ADAM_ComAdapt_Plot <- ADAM_ComAdapt_Plot %>% annotate_figure(top = text_grob("ADAM Adapt Parameters", color = "Black", face = "bold", size = 40))
ADAM_ComAdapt_Plot
```

```{r}
ADAM_ComJoint_Plot <- ggarrange(ADAM_Joint_Plot, ADAM_Joint_Plot_Com, ncol = 2, nrow = 1)
ADAM_ComJoint_Plot
ADAM_ComJoint_Plot <- ADAM_ComJoint_Plot %>% annotate_figure(top = text_grob("ADAM Joint Parameters", color = "Black", face = "bold", size = 40))
ADAM_ComJoint_Plot
```

```{r}
ADAM_Com_Plot <- ggarrange(ADAM_ComAdapt_Plot, ADAM_ComJoint_Plot, ncol = 2, nrow = 1)
ADAM_Com_Plot
ADAM_Com_Plot <- ADAM_Com_Plot %>% annotate_figure(top = text_grob("", color = "Black", face = "bold", size = 40))
ADAM_Com_Plot
```

#### _____________________ NOT TRANSFORMED PLOTS______________________________________________________________________
#### ___________________________________________________________________________________________________________________________
### Define split Adaptation Only plots

```{r}
Adapt_Alpha_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Adapt_Alpha, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Adapt_Alpha, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Adapt_Alpha, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightcoral', 'red','darkred')) +
  labs(x= NULL, y = "Phase Correction", fill = "")+
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none") +
  theme(axis.text.x = element_blank())

#Adapt_Alpha_plot
#ggsave("Adapt_Alpha_plot.png", dpi=600)


Adapt_Beta_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Adapt_Beta, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Adapt_Beta, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Adapt_Beta, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightsalmon', 'orange','darkorange')) +
  labs(x= NULL, y = "Period Correction", fill = "")+
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none") + 
  theme(axis.text.x = element_blank())

#Adapt_Beta_plot
#ggsave("Adapt_Beta_plot.png", dpi=600)


Adapt_Tn_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Adapt_Tn, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Adapt_Tn, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Adapt_Tn, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightgrey','darkgrey','black')) +
  labs(x= NULL, y = "Timekeeper Noise", fill = "")+
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none") + 
  theme(axis.text.x = element_blank())

#Adapt_Tn_plot
#ggsave("Adapt_Tn_plot.png", dpi=600)

Adapt_Mn_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Adapt_Mn, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Adapt_Mn, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Adapt_Mn, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightgrey','darkgrey','black')) +
  labs(x="Pair", y = "Motor Noise", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none")

#Adapt_Mn_plot
#ggsave("Adapt_Mn_plot.png", dpi=600)

# Adaptation only plot
ADAM_Adapt_Plot <- ggarrange(Adapt_Alpha_plot, Adapt_Beta_plot, 
                             Adapt_Tn_plot, Adapt_Mn_plot,
                             label.x = c(-.001, -.001, -.001, -.001),
                             label.y = c(1.03, 1.03, 1.03, 1.03),
                             font.label=list(color="black",size=24),
                             ncol = 1, nrow = 4
)
ADAM_Adapt_Plot
ADAM_Adapt_Plot <- ADAM_Adapt_Plot %>% annotate_figure(top = text_grob("Adaptation Only Model", color = "Black", face = "bold", size = 24))
ADAM_Adapt_Plot
```

### Define split Joint Only plots

```{r}
Joint_Beta_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Joint_Beta, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Joint_Beta, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Joint_Beta, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightsalmon', 'orange','darkorange')) +
  labs(x= NULL, y = "Period Correction", fill = "")+
  theme_bw() +
  adam_plot_specs +
  ylim(NA, 0.2) +
  guides(fill = "none") + 
  theme(axis.text.x = element_blank())


Joint_Delta_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Joint_Delta, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Joint_Delta, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Joint_Delta, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightblue','blue','royalblue')) +
  labs(x= NULL, y = "Temporal Prediction", fill = "")+
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none") + 
  theme(axis.text.x = element_blank())


Joint_Gamma_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Joint_Gamma, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Joint_Gamma, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Joint_Gamma, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightgreen','darkgreen','seagreen')) +
  labs(x= NULL, y = "Anticipatory Correction", fill = "")+
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none") + 
  theme(axis.text.x = element_blank())

Joint_Tn_plot <- all_data %>%
  mutate(Musicians_Present = fct_relevel(Musicians_Present, "12", "13", "23")) %>%
  ggplot(aes(y = Joint_Tn, x = Musicians_Present, fill = Musicians_Present, show.legend = TRUE)) +
  geom_flat_violin(position = position_nudge(x = .13, y = 0), alpha = .8) +
  geom_point(aes(y = Joint_Tn, x = Musicians_Present, fill = Musicians_Present), position=position_jitterdodge(jitter.width=0.05, dodge.width=0.1), shape = 21, size = 4, color = "black", alpha = 0.5, show.legend = FALSE) +
  geom_boxplot(aes(y = Joint_Tn, x = Musicians_Present, fill = Musicians_Present), position = position_dodgenudge(x=-.2), width = .25, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  expand_limits(x = 2) +
  #guides(fill = "none") +
  #guides(color = "none") +
  scale_fill_manual(values=c('lightgrey','darkgrey','black')) +
  labs(x="Pair", y = "Timekeeper Noise", fill = "")+
  scale_x_discrete("Pair", labels = c("Piano and Bass", "Piano and Drums", "Bass and Drums")) +
  theme_bw() +
  adam_plot_specs +
  guides(fill = "none")

# Adaptation only plot
ADAM_Joint_Plot <- ggarrange(Joint_Beta_plot, Joint_Delta_plot, 
                             Joint_Gamma_plot, Joint_Tn_plot,
                             label.x = c(-.001, -.001, -.001, -.001),
                             label.y = c(1.03, 1.03, 1.03, 1.03),
                             font.label=list(color="black",size=24),
                             ncol = 1, nrow = 4
)
ADAM_Joint_Plot
ADAM_Joint_Plot <- ADAM_Joint_Plot %>% annotate_figure(top = text_grob("Joint Model", color = "Black", face = "bold", size = 24))
ADAM_Joint_Plot
```

### Combine Plots

```{r}
ADAM_Split_Full_Plot <- ggarrange(ADAM_Adapt_Plot, ADAM_Joint_Plot, ncol = 2, nrow = 1)
ADAM_Split_Full_Plot
ADAM_Split_Full_Plot <- ADAM_Split_Full_Plot %>% annotate_figure(top = text_grob("ADAM Parameters - Pairwise", color = "Black", face = "bold", size = 40))
ADAM_Split_Full_Plot
```

# PLOT NOT PAIRWISE

```{r}
Adapt_Alpha_plot <- all_data %>%
  ggplot(aes(x = "", y = Adapt_Alpha)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'red', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'red', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'red', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Phase Correction" #Phase Correction
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Adapt_Beta_plot <- all_data %>%
  ggplot(aes(x = "", y = Adapt_Beta)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'orange', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'orange', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'orange', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Period Correction" #Period Correction
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Adapt_Tn_plot <- all_data %>%
  ggplot(aes(x = "", y = Adapt_Tn)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'grey', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'grey', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'grey', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Timekeeper Noise" #Timekeeper Noise
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Adapt_Mn_plot <- all_data %>%
  ggplot(aes(x = "", y = Adapt_Mn)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'grey', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'grey', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'grey', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Motor Noise" #Motor Noise
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


# Adaptation only plot
ADAM_Adapt_Plot_Com <- ggarrange(Adapt_Alpha_plot, Adapt_Beta_plot, 
                             Adapt_Tn_plot, Adapt_Mn_plot,  
                             label.x = c(-.001, -.001, -.001, -.001),
                             label.y = c(1.03, 1.03, 1.03, 1.03),
                             font.label=list(color="black",size=24),
                             ncol = 1, nrow = 4
)
ADAM_Adapt_Plot_Com
ADAM_Adapt_Plot_Com <- ADAM_Adapt_Plot_Com %>% annotate_figure(top = text_grob("Adaptation Only Model", color = "Black", face = "bold", size = 24))
ADAM_Adapt_Plot_Com
```

```{r}
Joint_Beta_plot <- all_data %>%
  ggplot(aes(x = "", y = Joint_Beta)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'orange', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'orange', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'orange', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Period Correction" #Period Correction
  ) +
  theme_bw() +
  ylim(NA, 0.2) +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Joint_Delta_plot <- all_data %>%
  ggplot(aes(x = "", y = Joint_Delta)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'blue', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'blue', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'blue', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Temporal Prediction" #Temporal Prediction
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Joint_Gamma_plot <- all_data %>%
  ggplot(aes(x = "", y = Joint_Gamma)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'darkgreen', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'darkgreen', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'darkgreen', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Anticipatory Correction" #Anticipatory Correction
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


Joint_Tn_plot <- all_data %>%
  ggplot(aes(x = "", y = Joint_Tn)) +
  geom_flat_violin(position = position_nudge(x = 0.15), fill = 'grey', alpha = 0.8) +
  geom_point(position = position_jitter(width = 0.05), shape = 21, size = 4,
             color = "black", fill = 'grey', alpha = 0.6) +
  geom_boxplot(position = position_nudge(x = -0.2), width = 0.2,
               outlier.shape = NA, fill = 'grey', alpha = 0.5) +
  labs(
    x = NULL,
    y = "Timekeeper Noise" #Timekeeper Noise
  ) +
  theme_bw() +
  raincloud_theme +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )


# Adaptation only plot
ADAM_Joint_Plot_Com <- ggarrange(Joint_Beta_plot, Joint_Delta_plot, 
                             Joint_Gamma_plot, Joint_Tn_plot,
                             label.x = c(-.001, -.001, -.001, -.001),
                             label.y = c(1.03, 1.03, 1.03, 1.03),
                             font.label=list(color="black",size=24),
                             ncol = 1, nrow = 4
)
ADAM_Joint_Plot_Com
ADAM_Joint_Plot_Com <- ADAM_Joint_Plot_Com %>% annotate_figure(top = text_grob("Joint Model", color = "Black", face = "bold", size = 24))
ADAM_Joint_Plot_Com
```
### Combine Plots

```{r}
ADAM_Full_Plot <- ggarrange(ADAM_Adapt_Plot_Com, ADAM_Joint_Plot_Com, ncol = 2, nrow = 1)
ADAM_Full_Plot
ADAM_Full_Plot <- ADAM_Full_Plot %>% annotate_figure(top = text_grob("ADAM Parameters", color = "Black", face = "bold", size = 40))
ADAM_Full_Plot
```

```{r}
ADAM_ComAdapt_Plot <- ggarrange(ADAM_Adapt_Plot, ADAM_Adapt_Plot_Com, ncol = 2, nrow = 1)
ADAM_ComAdapt_Plot
ADAM_ComAdapt_Plot <- ADAM_ComAdapt_Plot %>% annotate_figure(top = text_grob("ADAM Adapt Parameters", color = "Black", face = "bold", size = 40))
ADAM_ComAdapt_Plot
```

```{r}
ADAM_ComJoint_Plot <- ggarrange(ADAM_Joint_Plot, ADAM_Joint_Plot_Com, ncol = 2, nrow = 1)
ADAM_ComJoint_Plot
ADAM_ComJoint_Plot <- ADAM_ComJoint_Plot %>% annotate_figure(top = text_grob("ADAM Joint Parameters", color = "Black", face = "bold", size = 40))
ADAM_ComJoint_Plot
```

```{r}
ADAM_Com_Plot <- ggarrange(ADAM_ComAdapt_Plot, ADAM_ComJoint_Plot, ncol = 2, nrow = 1)
ADAM_Com_Plot
ADAM_Com_Plot <- ADAM_Com_Plot %>% annotate_figure(top = text_grob("", color = "Black", face = "bold", size = 40))
ADAM_Com_Plot
```