---
title: "Thesis ADAM Analysis 5"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

# ADAM Log-Likelihood Estimates

ADAM model parameter estimates were computed in Matlab script:

ThesisADAM_boundedresults.m Output is one file which includes participant and condition identifiers, a
range of performance measures, and parameter estimates for the
'Adaptation-only' and 'Full' versions of ADAM. Log-likelihood estimates
are also included for each model version, indicating quality of model
fit to data (higher values [less -vs/more +ve] mean better fit)

Adaptation-only version includes estimates of: 
- Phase Correction ('Adapt_Alpha') 
- Period Correction ('Adapt_Beta') 
- Timekeeper Noise ('Adapt_Tn') 
- Motor Noise ('Adapt_Mn')

Joint version of ADAM includes estimates of: 
- Period correction ('Joint_Beta') 
- Temporal Prediction ('Joint_Delta') 
- Anticipatory Error Correction ('Joint_Gamma') 
- Timekeeper Noise ('Joint_Tn')

Note that the ADAM parameter estimation procedure is run twice per data
set with TARGET musician (the one for which parameters are being
estimated) and REFERENCE musician (the one for which parameters are NOT
being estimated) swapped so estimates are given for each musician.

### Set directory where to read and write files

```{r}
setwd("C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis") # NEED TO SET TO CURRENT PATH
```

### Load libraries

```{r}
library(bestNormalize)
library(caret)
library(dplyr)
library(emmeans)
library(flextable)
library(ggeffects)
library(ggplot2)
library(ggpp) # for jitternudge [not currently used]
library(ggpubr)
library(ggsci) # For Raincloud plots
library(grid)
library(gridExtra)
library(gtools)
library(huxtable)
library(broom.mixed)
library(lme4) # For lmer
library(lmerTest) # Alternative for lmer that gives p-values/asterisks. Automatically updates output of lmer (just load here, no need to call below) 
library(reshape2)
library(rstatix)
library(stats) # For confint
library(tidyr)
library(tidyverse)
library(readxl)
library(CRSSIO) # This has additional custom editing features for boxplot
```

## Log-Likelihood estimates ----

### Plot boxplot

```{r}
lle_data_pairs <- all_data_pairs
lle_data_pairs <- lle_data_pairs %>%
  mutate(Musicians_Present = case_when(
    (MusicianA == 1 & MusicianB == 2) ~ "12",
    (MusicianA == 1 & MusicianB == 3) ~ "13",
    (MusicianA == 2 & MusicianB == 3) ~ "23",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(Musicians_Present))

# Now melt the summarized data
lle_adam_pairs <- melt(lle_data_pairs, id.vars = c('Song', 'Artist', 'MusicianA', 'MusicianB', 'Musicians_Present'), 
                     measure.vars = c('Adapt_LLE', 'Joint_LLE'), 
                     variable.name = 'Model_Version', value.name = "LLE")
```

```{r}
lle_data_group <- all_data_group

# Now melt the summarized data
lle_data_group <- melt(lle_data_group, id.vars = c('Song', 'Artist'), 
                     measure.vars = c('Adapt_LLE', 'Joint_LLE'), 
                     variable.name = 'Model_Version', value.name = "LLE")
```


```{r}
library(dplyr)
library(officer)
library(flextable)

# Define the filter threshold
threshold <- -750

# Count excluded values
excluded_counts <- lle_adam_pairs %>%
  filter(LLE <= threshold) %>%  # Excluded values
  count(Musicians_Present) %>%
  rename(`Musicians Present` = Musicians_Present, `Excluded Count` = n)

# Print excluded counts
print(excluded_counts)

# Now filter the data to keep only values with LLE > threshold
lle_filtered <- lle_adam_pairs %>%
  filter(LLE > threshold) %>%  # Keep only values above threshold
  mutate(Musicians_Present = factor(Musicians_Present, levels = c("12", "13", "23")))

# Convert to flextable and save in Word document
doc <- read_docx() %>%
  body_add_par("Number of Excluded Observations by Musicians Present", style = "heading 1") %>%
  body_add_flextable(flextable(excluded_counts))

# Save document
print(doc, target = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 5/Results/LLE_counts.docx")

# Count excluded values per group
excluded_counts <- lle_data_group %>%
  filter(LLE <= threshold) %>%  # This is the *excluded* part
  summarise(Excluded_Count = n())  # This counts how many rows are excluded

# Print to console (optional)
print(excluded_counts)

# Now filter the data to keep only values with LLE > threshold
llegroup_filtered <- lle_data_group %>%
  filter(LLE > threshold)  # Keep only values above threshold

# Convert to flextable and save in Word document
doc <- read_docx() %>%
  body_add_par("Number of Excluded Observations by Musicians Present", style = "heading 1") %>%
  body_add_flextable(flextable(excluded_counts))

# Save document
print(doc, target = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 5/Results/GroupLLE_counts.docx")
```


```{r}
LLE_ADAM_boxplot <- lle_filtered %>%
  mutate(Musicians_Present = factor(Musicians_Present, levels = c("12", "13", "23"))) %>%
  ggplot(aes(x = Musicians_Present, y = LLE, fill = Model_Version)) + 
  stat_boxplot_custom(aes(fill = Model_Version), qs = c(.05, .25, .5, .75, .95), outlier.shape = NA) +
  geom_jitter(aes(fill = Model_Version), 
              stat = "identity", show.legend = FALSE,
              position = position_jitterdodge(0.3), shape = 21, size = 3, color = "black", alpha = 0.5) +
  scale_fill_manual(name = "Model Version", labels = c('Adaptation Only', 'Full ADAM'), values = c('orange', 'royalblue')) +
  #coord_cartesian(ylim = c(-400, -300)) +  # Adjusted limits based on your LLE data
  labs(x = "Musicians Present", y = "Log Likelihood", fill = 'Model_Version') +
  theme_classic() +
  theme(panel.background = element_rect(fill = NA, color = "black", size = 1),
        panel.grid.major = element_blank(),
        axis.title = element_text(size = 24),
        axis.title.y = element_text(margin = margin(r = 6)),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.text = element_text(size = 20, color = "black"),
        legend.title = element_text(size = 24),
        legend.text = element_text(size = 20),
        legend.position = "none",
        legend.justification = "center",
        legend.box.margin = margin(0, 10, 0, 0))

LLE_ADAM_boxplot
```


```{r}
LLE_GroupADAM_boxplot <- llegroup_filtered %>%
  ggplot(aes(x = Model_Version, y = LLE, fill = Model_Version)) + 
  stat_boxplot_custom(aes(fill = Model_Version), qs = c(.05, .25, .5, .75, .95), outlier.shape = NA) +
  geom_jitter(aes(fill = Model_Version), 
              stat = "identity", show.legend = FALSE,
              position = position_jitterdodge(0.3), shape = 21, size = 3, color = "black", alpha = 0.5) +
  scale_fill_manual(name = "Model Version", labels = c('Adaptation Only', 'Full ADAM'), values = c('orange', 'royalblue')) +
  #coord_cartesian(ylim = c(-400, -300)) +  # Adjusted limits based on your LLE data
  labs(x = "Model Version", y = "Log Likelihood", fill = 'Model_Version') +
  theme_classic() +
  theme(panel.background = element_rect(fill = NA, color = "black", size = 1),
        panel.grid.major = element_blank(),
        axis.title = element_text(size = 24),
        axis.title.y = element_text(margin = margin(r = 6)),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.text = element_text(size = 20, color = "black"),
        legend.title = element_text(size = 24),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.justification = "center",
        legend.box.margin = margin(0, 10, 0, 0))

LLE_GroupADAM_boxplot

LLE_ADAM_boxplot_combined <- ggarrange(LLE_ADAM_boxplot, LLE_GroupADAM_boxplot,  
                                      labels = c("Pair-Wise", "Group-Wise"),
                                      label.x = c(.04, -.001),
                                      label.y = c(1.07, 1.07),
                                      font.label=list(color="black",size=26),
                                      ncol = 2, nrow = 1
)
LLE_ADAM_boxplot_combined
LLE_ADAM_boxplot_combined <- LLE_ADAM_boxplot_combined %>% annotate_figure(top = text_grob("Log-Likelihood Estimates
                                                                                           ", color = "Black", face = "bold", size = 36))
LLE_ADAM_boxplot_combined
```
```{r}
# Check for normality (for full data set, not averaged for trials within pairs)
all_data_lle <- melt(all_data, id.vars = c('Song', 'Artist', 'N_Events', 'Pair_Label', 'IOI_Entropy_z', 'Tempo_z'), 
                     measure.vars = c('Adapt_LLE', 'Joint_LLE'), 
                     variable.name = 'Model_Version', value.name = "LLE")

all_data_lle <- all_data_lle %>%
  group_by(Song, Artist, Pair_Label, Model_Version) %>%
  summarise(across(c(LLE, IOI_Entropy_z, Tempo_z, N_Events), mean, na.rm = TRUE))

ntestLLE <- shapiro.test(all_data_lle$LLE)
ntestLLE
bestNormalize(all_data_lle$LLE)
LLE_ON <- bestNormalize(all_data_lle$LLE)
all_data_lle$LLE_ON <- predict(LLE_ON, all_data_lle$LLE)
shapiro.test(all_data_lle$LLE_ON)
```


```{r}
#Full LMER model
lle_adam.lmer <- lmer(LLE_ON ~ Model_Version * IOI_Entropy_z * Pair_Label * Tempo_z + (1 | Artist/Song) + (1 | N_Events), data = all_data_lle, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
lle_adam_output <- summary(lle_adam.lmer)
lle_adam_output
capture.output(lle_adam_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 5/Results/lle_adam_LMER_output.txt") # Write output to text file

#lle_adam_lmer.ci <- confint(lle_adam.lmer)
#lle_adam_lmer.ci
#capture.output(lle_adam_lmer.ci, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script #5/lle_adam_lmer_CI.txt") # Write output to text file

# Reduced LMER model
lle_adam_reduced.lmer <- lmer(LLE_ON ~ 1 + + (1 | Artist/Song) + (1 | N_Events), data = all_data_lle, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
lle_lmer_output_reduced <- summary(lle_adam_reduced.lmer)
lle_lmer_output_reduced
capture.output(lle_lmer_output_reduced, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 5/lle_lmer_reduced_LMER_output.txt") # Write output to text file

# Compare the full and reduced models
lle_lmer_comparison <- anova(lle_adam.lmer, lle_adam_reduced.lmer)
lle_lmer_comparison
capture.output(lle_lmer_comparison, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 5/lle_LMER_comparison_output.txt") # Write output to text file

# Make output table
lle_adam.table <- huxreg(lle_adam.lmer, lle_adam_reduced.lmer, statistics = NULL, number_format = 2)
lle_adam.table
huxtable::quick_docx(lle_adam.table, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 5/lle_adam_table.docx") # Make Word table (not standardized coefficients)
```
