---
title: "Thesis ADAM Analysis 6"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

# ADAM Parameters Predict Asynchrony

ADAM model parameter estimates were computed in Matlab script:

ThesisADAM_boundedresults.m Output is one file which includes participant and condition identifiers, a
range of performance measures, and parameter estimates for the
'Adaptation-only' and 'Full' versions of ADAM. Log-likelihood estimates
are also included for each model version, indicating quality of model
fit to data (higher values [less -vs/more +ve] mean better fit)

Adaptation-only version includes estimates of: 
- Phase Correction ('Adapt_Alpha') 
- Period Correction ('Adapt_Beta') 
- Timekeeper Noise ('Adapt_Tn') 
- Motor Noise ('Adapt_Mn')

Joint version of ADAM includes estimates of: 
- Period correction ('Joint_Beta') 
- Temporal Prediction ('Joint_Delta') 
- Anticipatory Error Correction ('Joint_Gamma') 
- Timekeeper Noise ('Joint_Tn')

Note that the ADAM parameter estimation procedure is run twice per data
set with TARGET musician (the one for which parameters are being
estimated) and REFERENCE musician (the one for which parameters are NOT
being estimated) swapped so estimates are given for each musician.

### Set directory where to read and write files

```{r}
setwd("C:/Users/marc1/OneDrive/Desktop/Research/Aarhus University/Keller Work/Piano Duos") # NEED TO SET TO CURRENT PATH
```

### Load libraries

```{r}
library(bestNormalize)
library(caret)
library(dplyr)
library(emmeans)
library(flextable)
library(ggeffects)
library(ggplot2)
library(ggpp) # for jitternudge [not currently used]
library(ggpubr)
library(ggsci) # For Raincloud plots
library(grid)
library(gridExtra)
library(gtools)
library(huxtable)
library(broom.mixed)
library(lme4) # For lmer
library(lmerTest) # Alternative for lmer that gives p-values/asterisks. Automatically updates output of lmer (just load here, no need to call below) 
library(reshape2)
library(rstatix)
library(stats) # For confint
library(tidyr)
library(tidyverse)
library(readxl)
library(CRSSIO) # This has additional custom editing features for boxplot
```

```{r}
# ADAPTATION-ONLY ADAM
# Adapt Main LMER model predicting Asynchrony
Adapt.lmer <- lmer(DV_Async_ON ~ IOI_Entropy_z * Pair_Label * Tempo_z * (Adapt_Alpha_ON + Adapt_Beta_ON + Adapt_Tn_ON + Adapt_Mn_ON) + (1 | Artist/Song) + (1 | N_Events), data = all_data, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Adapt.lmer_output <- summary(Adapt.lmer)
Adapt.lmer_output
capture.output(Adapt.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Adapt_Param_LMER_output.txt") # Write output to text file

# Random Effects LMER model
Adapt_random.lmer <- lmer(DV_Async_ON ~ 1 +  (1 | Artist/Song) + (1 | N_Events), data = all_data, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Adapt_random.lmer_output <- summary(Adapt_random.lmer)
Adapt_random.lmer_output
capture.output(Adapt_random.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Adapt_Param_random_LMER_output.txt") # Write output to text file

# Compare full and reduced models 
Adapt_models_comparison <- anova(Adapt.lmer, Adapt_random.lmer)
Adapt_models_comparison
capture.output(Adapt_models_comparison, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Adapt_Param_comparison.txt") # Write output to text file

Adapt.table <- huxreg(Adapt.lmer, Adapt_random.lmer, statistics = NULL, number_format = 3)
Adapt.table
huxtable::quick_docx(Adapt.table, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Adapt_Param_table.docx") # Make Word table (not standardized coefficients)

# JOINT ADAM
# Joint Main LMER model predicting Asynchrony (NB: Runs into convergence and singularity issues if Condition*Tn interaction is included)
Joint.lmer <- lmer(DV_Async_ON ~ IOI_Entropy_z * Pair_Label * Tempo_z * (Joint_Beta_ON + Joint_Delta_ON + Joint_Gamma_ON + Joint_Tn_ON) + (1 | Artist/Song) + (1 | N_Events), data = all_data, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Joint.lmer_output <- summary(Joint.lmer)
Joint.lmer_output
capture.output(Joint.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Joint_Param_LMER_output.txt") # Write output to text file

# Random Effects LMER model
Joint_random.lmer <- lmer(DV_Async_ON ~ 1 + (1 | Artist/Song) + (1 | N_Events), data = all_data, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Joint_random.lmer_output <- summary(Joint_random.lmer)
Joint_random.lmer_output
capture.output(Joint_random.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Joint_Param_random_LMER_output") # Write output to text file

# Compare full and reduced models 
Joint_models_comparison <- anova(Joint.lmer, Joint_random.lmer)
Joint_models_comparison
capture.output(Joint_models_comparison, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Joint_Param_comparison.txt") # Write output to text file


Joint.table <- huxreg(Joint.lmer, Joint_random.lmer, statistics = NULL, number_format = 3)
Joint.table
huxtable::quick_docx(Joint.table, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Joint_Param_table.docx") # Make Word table (not standardized coefficients)
```

## Plots of ADAM parameters predicting Asynchrony

```{r}
indiv_adam_adapt_alpha_tran.effects <- ggemmeans(Adapt.lmer, c("Adapt_Alpha_ON"))
indiv_adam_adapt_alpha_tran.plot <- plot(indiv_adam_adapt_alpha_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL, colors = "red") +
  labs(x= "Phase Correction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) 
  scale_color_manual(values = c("red")) +
  scale_fill_manual(values = c("red")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_adapt_alpha_tran.plot$layers)) {
  indiv_adam_adapt_alpha_tran.plot$layers[[i]]$aes_params$colour <- "red"
  indiv_adam_adapt_alpha_tran.plot$layers[[i]]$aes_params$fill <- "red"
}
indiv_adam_adapt_alpha_tran.plot

indiv_adam_adapt_beta_tran.effects <- ggemmeans(Adapt.lmer, c("Adapt_Beta_ON"))
indiv_adam_adapt_beta_tran.plot <- plot(indiv_adam_adapt_beta_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL, colors = 'darkorange') +
  labs(x= "Period Correction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("darkorange","darkorange")) +
  scale_fill_manual(values= c("darkorange","darkorange")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_adapt_beta_tran.plot$layers)) {
  indiv_adam_adapt_beta_tran.plot$layers[[i]]$aes_params$colour <- "darkorange"
  indiv_adam_adapt_beta_tran.plot$layers[[i]]$aes_params$fill <- "darkorange"
}
indiv_adam_adapt_beta_tran.plot

indiv_adam_adapt_Tn_tran.effects <- ggemmeans(Adapt.lmer, c("Adapt_Tn_ON"))
indiv_adam_adapt_Tn_tran.plot <- plot(indiv_adam_adapt_Tn_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL, colors = 'black') +
  labs(x= "Timekeeper Noise Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("black","black")) +
  scale_fill_manual(values= c("black","black")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_adapt_Tn_tran.plot$layers)) {
  indiv_adam_adapt_Tn_tran.plot$layers[[i]]$aes_params$colour <- "black"
  indiv_adam_adapt_Tn_tran.plot$layers[[i]]$aes_params$fill <- "black"
}
indiv_adam_adapt_Tn_tran.plot

indiv_adam_adapt_Mn_tran.effects <- ggemmeans(Adapt.lmer, c("Adapt_Mn_ON"))
indiv_adam_adapt_Mn_tran.plot <- plot(indiv_adam_adapt_Mn_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Motor Noise Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("darkgrey","darkgrey")) +
  scale_fill_manual(values= c("darkgrey","darkgrey")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_adapt_Mn_tran.plot$layers)) {
  indiv_adam_adapt_Mn_tran.plot$layers[[i]]$aes_params$colour <- "darkgrey"
  indiv_adam_adapt_Mn_tran.plot$layers[[i]]$aes_params$fill <- "darkgrey"
}
indiv_adam_adapt_Mn_tran.plot

# Combined plot

# Adaptation only plot
Adapt_Effect_plot <- ggarrange(indiv_adam_adapt_alpha_tran.plot, indiv_adam_adapt_beta_tran.plot, 
                               indiv_adam_adapt_Tn_tran.plot, indiv_adam_adapt_Mn_tran.plot,  
                                 #labels = c("A", "B", "C", "D"),
                                 label.x = c(-.001, -.001, -.001, -.001),
                                 label.y = c(1.09, 1.09, 1.09, 1.09),
                                 font.label=list(color="black",size=24),
                                 ncol = 1, nrow = 4
)
Adapt_Effect_plot
Adapt_Effect_plot <- Adapt_Effect_plot %>% annotate_figure(top = text_grob("Combined", color = "Black", face = "bold", size = 24))
Adapt_Effect_plot
```

```{r}
# Full ADAM
indiv_adam_full_beta_tran.effects <- ggemmeans(Joint.lmer, c("Joint_Beta_ON"))
indiv_adam_full_beta_tran.plot <- plot(indiv_adam_full_beta_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Period Correction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("darkorange","darkorange")) +
  scale_fill_manual(values= c("darkorange","darkorange")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_full_beta_tran.plot$layers)) {
  indiv_adam_full_beta_tran.plot$layers[[i]]$aes_params$colour <- "darkorange"
  indiv_adam_full_beta_tran.plot$layers[[i]]$aes_params$fill <- "darkorange"
}
indiv_adam_full_beta_tran.plot

indiv_adam_full_delta_tran.effects <- ggemmeans(Joint.lmer, c("Joint_Delta_ON"))
indiv_adam_full_delta_tran.plot <- plot(indiv_adam_full_delta_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Temporal Prediction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("blue","blue")) +
  scale_fill_manual(values= c("blue","blue")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_full_delta_tran.plot$layers)) {
  indiv_adam_full_delta_tran.plot$layers[[i]]$aes_params$colour <- "blue"
  indiv_adam_full_delta_tran.plot$layers[[i]]$aes_params$fill <- "blue"
}
indiv_adam_full_delta_tran.plot

indiv_adam_full_gamma_tran.effects <- ggemmeans(Joint.lmer, c("Joint_Gamma_ON"))
indiv_adam_full_gamma_tran.plot <- plot(indiv_adam_full_gamma_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Anticipatory Correction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("darkgreen","darkgreen")) +
  scale_fill_manual(values= c("darkgreen","darkgreen")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_full_gamma_tran.plot$layers)) {
  indiv_adam_full_gamma_tran.plot$layers[[i]]$aes_params$colour <- "darkgreen"
  indiv_adam_full_gamma_tran.plot$layers[[i]]$aes_params$fill <- "darkgreen"
}
indiv_adam_full_gamma_tran.plot

indiv_adam_full_Tn_tran.effects <- ggemmeans(Joint.lmer, c("Joint_Tn_ON"))
indiv_adam_full_Tn_tran.plot <- plot(indiv_adam_full_Tn_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Timekeeper Noise Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("black","black")) +
  scale_fill_manual(values= c("black","black")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_full_Tn_tran.plot$layers)) {
  indiv_adam_full_Tn_tran.plot$layers[[i]]$aes_params$colour <- "black"
  indiv_adam_full_Tn_tran.plot$layers[[i]]$aes_params$fill <- "black"
}
indiv_adam_full_Tn_tran.plot

# Combined plot
# Full ADAM plot
Joint_Effect_plot <- ggarrange(indiv_adam_full_beta_tran.plot, indiv_adam_full_delta_tran.plot, 
                               indiv_adam_full_gamma_tran.plot, indiv_adam_full_Tn_tran.plot,
                                #labels = c("E", "F", "G", "H"),
                                label.x = c(-.001, -.001, -.001, -.001),
                                label.y = c(1.09, 1.09, 1.09, 1.09),
                                font.label=list(color="black",size=24),
                                ncol = 1, nrow = 4)
Joint_Effect_plot
Joint_Effect_plot <- Joint_Effect_plot %>% annotate_figure(top = text_grob("Combined", color = "Black", face = "bold", size = 24))
Joint_Effect_plot
```
#___________________________GROUP LEVEL____________________________________________________
```{r}
# ADAPTATION-ONLY ADAM
# Adapt Main LMER model predicting Asynchrony
Adapt.lmer <- lmer(Group_Async_ON ~ IOI_Entropy_Global_z * Tempo_z * (Adapt_Alpha_ON + Adapt_Beta_ON + Adapt_Tn_ON + Adapt_Mn_ON) + (1 | Artist) + (1 | Song) + (1 | N_Events), data = all_data_group, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Adapt.lmer_output <- summary(Adapt.lmer)
Adapt.lmer_output
capture.output(Adapt.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Group_Adapt_Param_LMER_output.txt") # Write output to text file

# Random Effects LMER model
Adapt_random.lmer <- lmer(Group_Async_ON ~ 1 + (1 | Artist) + (1 | Song) + (1 | N_Events), data = all_data_group, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Adapt_random.lmer_output <- summary(Adapt_random.lmer)
Adapt_random.lmer_output
capture.output(Adapt_random.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Group_Adapt_Param_random_LMER_output.txt") # Write output to text file

# Compare full and reduced models 
Adapt_models_comparison <- anova(Adapt.lmer, Adapt_random.lmer)
Adapt_models_comparison
capture.output(Adapt_models_comparison, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Group_Adapt_Param_comparison.txt") # Write output to text file

Adapt.table <- huxreg(Adapt.lmer, Adapt_random.lmer, statistics = NULL, number_format = 3)
Adapt.table
huxtable::quick_docx(Adapt.table, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Group_Adapt_Param_table.docx") # Make Word table (not standardized coefficients)

# JOINT ADAM
# Joint Main LMER model predicting Asynchrony (NB: Runs into convergence and singularity issues if Condition*Tn interaction is included)
Joint.lmer <- lmer(Group_Async_ON ~ IOI_Entropy_Global_z * Tempo_z * (Joint_Beta_ON + Joint_Delta_ON + Joint_Gamma_ON + Joint_Tn_ON) + (1 | Artist) + (1 | Song) + (1 | N_Events), data = all_data_group, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Joint.lmer_output <- summary(Joint.lmer)
Joint.lmer_output
capture.output(Joint.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Group_Joint_Param_LMER_output.txt") # Write output to text file

# Random Effects LMER model
Joint_random.lmer <- lmer(Group_Async_ON ~ 1 + (1 | Artist) + (1 | Song) + (1 | N_Events), data = all_data_group, control = lmerControl(optimizer = "bobyqa"), REML = FALSE)
Joint_random.lmer_output <- summary(Joint_random.lmer)
Joint_random.lmer_output
capture.output(Joint_random.lmer_output, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Group_Joint_Param_random_LMER_output") # Write output to text file

# Compare full and reduced models 
Joint_models_comparison <- anova(Joint.lmer, Joint_random.lmer)
Joint_models_comparison
capture.output(Joint_models_comparison, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Group_Joint_Param_comparison.txt") # Write output to text file


Joint.table <- huxreg(Joint.lmer, Joint_random.lmer, statistics = NULL, number_format = 3)
Joint.table
huxtable::quick_docx(Joint.table, file = "C:/Users/marc1/OneDrive/Desktop/School/Aarhus University/Current Classes/Thesis/Analysis/Outputs/Script 6/Group_Joint_Param_table.docx") # Make Word table (not standardized coefficients)
```

## Plots of ADAM parameters predicting Asynchrony

```{r}
indiv_adam_adapt_alpha_tran.effects <- ggemmeans(Adapt.lmer, c("Adapt_Alpha_ON"))
indiv_adam_adapt_alpha_tran.plot <- plot(indiv_adam_adapt_alpha_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL, colors = "red") +
  labs(x= "Phase Correction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) 
  scale_color_manual(values = c("red")) +
  scale_fill_manual(values = c("red")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_adapt_alpha_tran.plot$layers)) {
  indiv_adam_adapt_alpha_tran.plot$layers[[i]]$aes_params$colour <- "red"
  indiv_adam_adapt_alpha_tran.plot$layers[[i]]$aes_params$fill <- "red"
}
indiv_adam_adapt_alpha_tran.plot

indiv_adam_adapt_beta_tran.effects <- ggemmeans(Adapt.lmer, c("Adapt_Beta_ON"))
indiv_adam_adapt_beta_tran.plot <- plot(indiv_adam_adapt_beta_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL, colors = 'darkorange') +
  labs(x= "Period Correction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("darkorange","darkorange")) +
  scale_fill_manual(values= c("darkorange","darkorange")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_adapt_beta_tran.plot$layers)) {
  indiv_adam_adapt_beta_tran.plot$layers[[i]]$aes_params$colour <- "darkorange"
  indiv_adam_adapt_beta_tran.plot$layers[[i]]$aes_params$fill <- "darkorange"
}
indiv_adam_adapt_beta_tran.plot

indiv_adam_adapt_Tn_tran.effects <- ggemmeans(Adapt.lmer, c("Adapt_Tn_ON"))
indiv_adam_adapt_Tn_tran.plot <- plot(indiv_adam_adapt_Tn_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL, colors = 'black') +
  labs(x= "Timekeeper Noise Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("black","black")) +
  scale_fill_manual(values= c("black","black")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_adapt_Tn_tran.plot$layers)) {
  indiv_adam_adapt_Tn_tran.plot$layers[[i]]$aes_params$colour <- "black"
  indiv_adam_adapt_Tn_tran.plot$layers[[i]]$aes_params$fill <- "black"
}
indiv_adam_adapt_Tn_tran.plot

indiv_adam_adapt_Mn_tran.effects <- ggemmeans(Adapt.lmer, c("Adapt_Mn_ON"))
indiv_adam_adapt_Mn_tran.plot <- plot(indiv_adam_adapt_Mn_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Motor Noise Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("darkgrey","darkgrey")) +
  scale_fill_manual(values= c("darkgrey","darkgrey")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_adapt_Mn_tran.plot$layers)) {
  indiv_adam_adapt_Mn_tran.plot$layers[[i]]$aes_params$colour <- "darkgrey"
  indiv_adam_adapt_Mn_tran.plot$layers[[i]]$aes_params$fill <- "darkgrey"
}
indiv_adam_adapt_Mn_tran.plot

# Combined plot

# Adaptation only plot
Adapt_Effect_plot <- ggarrange(indiv_adam_adapt_alpha_tran.plot, indiv_adam_adapt_beta_tran.plot, 
                               indiv_adam_adapt_Tn_tran.plot, indiv_adam_adapt_Mn_tran.plot,  
                                 #labels = c("A", "B", "C", "D"),
                                 label.x = c(-.001, -.001, -.001, -.001),
                                 label.y = c(1.09, 1.09, 1.09, 1.09),
                                 font.label=list(color="black",size=24),
                                 ncol = 1, nrow = 4
)
Adapt_Effect_plot
Adapt_Effect_plot <- Adapt_Effect_plot %>% annotate_figure(top = text_grob("Combined", color = "Black", face = "bold", size = 24))
Adapt_Effect_plot
```

```{r}
# Full ADAM
indiv_adam_full_beta_tran.effects <- ggemmeans(Joint.lmer, c("Joint_Beta_ON"))
indiv_adam_full_beta_tran.plot <- plot(indiv_adam_full_beta_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Period Correction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("darkorange","darkorange")) +
  scale_fill_manual(values= c("darkorange","darkorange")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_full_beta_tran.plot$layers)) {
  indiv_adam_full_beta_tran.plot$layers[[i]]$aes_params$colour <- "darkorange"
  indiv_adam_full_beta_tran.plot$layers[[i]]$aes_params$fill <- "darkorange"
}
indiv_adam_full_beta_tran.plot

indiv_adam_full_delta_tran.effects <- ggemmeans(Joint.lmer, c("Joint_Delta_ON"))
indiv_adam_full_delta_tran.plot <- plot(indiv_adam_full_delta_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Temporal Prediction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("blue","blue")) +
  scale_fill_manual(values= c("blue","blue")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_full_delta_tran.plot$layers)) {
  indiv_adam_full_delta_tran.plot$layers[[i]]$aes_params$colour <- "blue"
  indiv_adam_full_delta_tran.plot$layers[[i]]$aes_params$fill <- "blue"
}
indiv_adam_full_delta_tran.plot

indiv_adam_full_gamma_tran.effects <- ggemmeans(Joint.lmer, c("Joint_Gamma_ON"))
indiv_adam_full_gamma_tran.plot <- plot(indiv_adam_full_gamma_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Anticipatory Correction Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("darkgreen","darkgreen")) +
  scale_fill_manual(values= c("darkgreen","darkgreen")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_full_gamma_tran.plot$layers)) {
  indiv_adam_full_gamma_tran.plot$layers[[i]]$aes_params$colour <- "darkgreen"
  indiv_adam_full_gamma_tran.plot$layers[[i]]$aes_params$fill <- "darkgreen"
}
indiv_adam_full_gamma_tran.plot

indiv_adam_full_Tn_tran.effects <- ggemmeans(Joint.lmer, c("Joint_Tn_ON"))
indiv_adam_full_Tn_tran.plot <- plot(indiv_adam_full_Tn_tran.effects, show_residuals = TRUE, alpha = .2, dot_alpha = .5, dot_size = 2, limit_range = FALSE, jitter = NULL) +
  labs(x= "Timekeeper Noise Estimate (ON)", y = "Residual Async. (ON)", title = "") +
  #coord_cartesian(ylim = c(0, 150)) +
  scale_colour_manual(values = c("black","black")) +
  scale_fill_manual(values= c("black","black")) +
  theme_bw() +
  theme(panel.grid = element_blank())
for (i in seq_along(indiv_adam_full_Tn_tran.plot$layers)) {
  indiv_adam_full_Tn_tran.plot$layers[[i]]$aes_params$colour <- "black"
  indiv_adam_full_Tn_tran.plot$layers[[i]]$aes_params$fill <- "black"
}
indiv_adam_full_Tn_tran.plot

# Combined plot
# Full ADAM plot
Joint_Effect_plot <- ggarrange(indiv_adam_full_beta_tran.plot, indiv_adam_full_delta_tran.plot, 
                               indiv_adam_full_gamma_tran.plot, indiv_adam_full_Tn_tran.plot,
                                #labels = c("E", "F", "G", "H"),
                                label.x = c(-.001, -.001, -.001, -.001),
                                label.y = c(1.09, 1.09, 1.09, 1.09),
                                font.label=list(color="black",size=24),
                                ncol = 1, nrow = 4)
Joint_Effect_plot
Joint_Effect_plot <- Joint_Effect_plot %>% annotate_figure(top = text_grob("Combined", color = "Black", face = "bold", size = 24))
Joint_Effect_plot
```